---
title: 'PEB Validity With Reduced DEEP CTN Scale (Pilot 1 SONA Spr23)'
author: Deb Lindsay
date: "`r Sys.Date()`"
slug: PEB_validity_sp23_reduced
categories:
  - Validity
tags:
  - Connection to Nature
  - DEEP CTN
  - Paper 1
  - Pro-Environmental Behavior
subtitle: ''
summary: ''
authors: []
lastmod: "`r Sys.Date()`"
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
output:
  blogdown::html_page:
    toc: true
editor_options: 
  markdown: 
    wrap: 72
---
```{r Packages and Functions required, include=FALSE}

library(tidyverse) #base package that runs most functions
library(flextable) #tables
library(corrplot) #correlations
library(Hmisc) #correlations 
library(car) # Type 2 Anova
library(effectsize) #effect sizes
library(ggplot2) #plots
library(relaimpo) #calculates unique variance
library(gridExtra) # better figure layouts
```

```{r loading data, include=FALSE}
CFA1 <- 
     read_csv("../2023-12-14-cfa-data/CFApilot1SONA_data_clean.csv")

#pull out non-binary participants as the n is not big enough to run analyses
#removed 9 participants
CFA1 <-    
 CFA1 %>% 
     filter(gender == "Woman" | gender == "Man") 

#create new measure based on CFA pilot 1
# Reduced DEEP CTN scale with only 20 items
val_data <-
     CFA1 %>% 
     mutate(deep_ctn = (DEEPCTN_s_1 + 
                             DEEPCTN_s_2 +
                             DEEPCTN_s_3 +
                             DEEPCTN_s_7 +
                             DEEPCTN_s_8)/5,
            deep_ctn_z = as.numeric(scale(deep_ctn, 
                                          center = T, scale = T)),
            exp_CTN = (DEEPCTN_ex_4 +
                            DEEPCTN_ex_5 +
                            DEEPCTN_ex_1 +
                            DEEPCTN_ex_2 +
                            DEEPCTN_ex_3)/5,
            exp_ctn_z = as.numeric(scale(exp_CTN, 
                                         center = T, scale = T)),
            
            emo_CTN = (DEEPCTN_emo_1 +
                            DEEPCTN_emo_2 +
                            DEEPCTN_emo_3 +
                            DEEPCTN_emo_4 +
                            DEEPCTN_em_6)/5,
            emo_ctn_z = as.numeric(scale(emo_CTN,
                                         center = T, scale = T)),
            
            presc_CTN = (DEEPCTN_m_1 +
                              DEEPCTN_m_2 +
                              DEEPCTN_m_4 +
                              DEEPCTN_m_5 +
                              DEEPCTN_m_6)/5,
            presc_ctn_z = as.numeric(scale(presc_CTN, 
                                           center = T, scale = T)),
            
            CTN_overall = ((DEEPCTN_s_1 + 
                             DEEPCTN_s_2 +
                             DEEPCTN_s_3 +
                             DEEPCTN_s_7 +
                             DEEPCTN_s_8+
                             DEEPCTN_ex_4 +
                            DEEPCTN_ex_5 +
                            DEEPCTN_ex_1 +
                            DEEPCTN_ex_2 +
                            DEEPCTN_ex_3 +
                            DEEPCTN_emo_1 +
                            DEEPCTN_emo_2 +
                            DEEPCTN_emo_3 +
                            DEEPCTN_emo_4 +
                            DEEPCTN_em_6 +
                            DEEPCTN_m_1 +
                              DEEPCTN_m_2 +
                              DEEPCTN_m_4 +
                              DEEPCTN_m_5 +
                              DEEPCTN_m_6  )/20),
            CTN_overall_z = as.numeric(scale(CTN_overall, 
                                             center = T, scale = T)))

```

Pilot data collected during the Spring quarter (2023) on SONA students.
This was piloting the CFA that will be run on Prolific participants Jan
2024. See [DEEP CTN CFA](/post/cfa_sp23/) for descriptives from this
sample.

# Convergent Validity

We assessed the convergent validity of the new DEEP CTN scale, that is
how closely our new measure is related to other established measures of
the same construct. We tested this by looking at the zero order
correlation between our new measure and its subscales and two
established measures: The Connectedness to Nature Scale (CNS - Mayer &
Franz, 2004) and the Environmental Identity Scale revised (EID-R -
Clayton et al., 2021)

```{r Validation, include=FALSE}

cormatrix <- 
     val_data %>% 
          dplyr::select(CTN_overall_z,
                 deep_ctn_z,
                 exp_ctn_z,
                 emo_ctn_z,
                 presc_ctn_z,
                 CNS_Z,
                 EIDR_Z,
                 PEB_Z) %>% 
          as.matrix() 
            
correlations <-
     rcorr(cormatrix, type = "spearman")

corp <- 
     cor.mtest(cormatrix)

#Corplot
# I edited the Corplot function to move the significance stars up
# https://stackoverflow.com/questions/49695113/changing-the-position-of-the-signifigance-pch-symbols-in-corrplot
# 
# trace(corrplot, edit = T)
# 
# Then replace on line 443
#   place_points = function(sig.locs, point) {
#    text(pos.pNew[, 1][sig.locs], pos.pNew[, 2][sig.locs], 
#        labels = point, col = pch.col, cex = pch.cex, 
#        lwd = 2)
# 
#  with:
# adjust text(X,Y ...) according to your needs, here +0.25 is added to the Y-position    
# 
#    place_points = function(sig.locs, point) {
#      text(pos.pNew[, 1][sig.locs], (pos.pNew[, 2][sig.locs])+0.25, 
#           labels = point, col = pch.col, cex = pch.cex, 
#          lwd = 2)




```

```{r Correlation plot, echo=FALSE, include=TRUE, out.width="100%"}
#corrplot(correlations$r,
#         type = "upper",
#         method = "color",
#         addCoef.col = "black",
#         number.cex = .75,
#         outline = T,
#         addgrid.col = "white",
#         order = "original",
#         tl.cex = 1,
#         tl.col = "black",
#         tl.srt = 35,
#         cl.pos = "n",
#         p.mat = corp$p,
#         sig.level = c(0.001, 0.01, 0.05),
#         insig = "label_sig",
#         pch.cex = .75)

vars = c("CTN Overall", "Deep", "Experiential", "Emotional", "Presence", "CNS (Mayer & Frantz, 2004)", "EID-R (Clayton et al., 2021)", "PEB (Brick et al., 2017)")

nm = rownames(correlations$r)
m = t(combn(nm, 2))
d = cbind(data.frame(m), R = correlations$r[m], P = correlations$P[m])
d$label = round(d$R, 2)
d$label[d$P < 0.001] = paste0(d$label[d$P < 0.001], "\n**")
d$X1 = factor(d$X1, nm, labels = vars)
d$X2 = factor(d$X2, rev(nm), labels = rev(vars))



graphics.off()
validation_plot <- 
  ggplot(d, aes(X1, X2, fill = R, label = label)) +
    geom_tile(color = "white") +
    scale_fill_viridis_c() +
    geom_text(color = ifelse(d$R > 0.50, "black", "white"), size = 2) +
    theme_bw() +
    coord_equal() +
     theme(axis.text.x = element_text(angle = 45, hjust = 1),
           axis.title = element_blank(),
           panel.background = element_rect(fill='transparent'), #transparent panel bg
    plot.background = element_rect(fill='transparent', color=NA), #transparent plot bg
    panel.grid.major = element_blank(), #remove major gridlines
    panel.grid.minor = element_blank(), #remove minor gridlines
    legend.background = element_rect(fill='transparent'), #transparent legend bg
    legend.box.background = element_rect(fill='transparent') #transparent legend panel
  ) 


```

```{r validation plot 2, echo=FALSE}
print(validation_plot)



```
```{r cor plots, include=FALSE}
# deep_ctn_z - #77AB90
# exp_ctn_z - #2D99B1
# emo_ctn_z - #EC8C65
# presc_ctn_z - #F9C36C

deep_plot <- 
val_data %>% 
  ggplot() +
  geom_point(aes(y = PEB_Z, x = deep_ctn_z), colour = "#77AB90") + #deep
  geom_smooth(aes(y = PEB_Z, x = deep_ctn_z), method = "lm", colour = "#77AB90")+
  xlab(label = "Deep CTN") +
  ylab(label = "Pro-Environmental Behavior") +
  theme(panel.background = element_rect(fill='transparent'), 
        plot.background = element_rect(fill='transparent', color=NA), 
        panel.grid.major = element_line(colour = "#ECEFF2"),
        panel.grid.minor = element_blank())

#element_line(colour = "#ECEFF2")
exp_plot <- 
val_data %>% 
  ggplot() +
  geom_point(aes(y = PEB_Z, x = exp_ctn_z), colour = "#2D99B1") + #experiential
  geom_smooth(aes(y = PEB_Z, x = exp_ctn_z), method = "lm", colour = "#2D99B1") +
  xlab(label = "Experiential CTN") +
  ylab(label = "Pro-Environmental Behavior") +
    theme(panel.background = element_rect(fill='transparent'), 
        plot.background = element_rect(fill='transparent', color=NA), 
        panel.grid.major = element_line(colour = "#ECEFF2"),
        panel.grid.minor = element_blank())

emo_plot <- 
val_data %>% 
  ggplot() +
  geom_point(aes(y = PEB_Z, x = emo_ctn_z), colour = "#EC8C65") + #emotional
  geom_smooth(aes(y = PEB_Z, x = emo_ctn_z), method = "lm", colour = "#EC8C65") +
  xlab(label = "Emotional CTN") +
  ylab(label = "Pro-Environmental Behavior") +
    theme(panel.background = element_rect(fill='transparent'), 
        plot.background = element_rect(fill='transparent', color=NA), 
        panel.grid.major = element_line(colour = "#ECEFF2"),
        panel.grid.minor = element_blank())

presence_plot <- 
val_data %>% 
  ggplot() +
  geom_point(aes(y = PEB_Z, x = presc_ctn_z), colour = "#F9C36C") + #presence
  geom_smooth(aes(y = PEB_Z, x = presc_ctn_z), method = "lm", colour = "#F9C36C") +
  xlab(label = "Presence CTN") +
  ylab(label = "Pro-Environmental Behavior") +
    theme(panel.background = element_rect(fill='transparent'), 
        plot.background = element_rect(fill='transparent', color=NA), 
        panel.grid.major = element_line(colour = "#ECEFF2"),
        panel.grid.minor = element_blank())

cor_plots <- 
grid.arrange(deep_plot, exp_plot, emo_plot, presence_plot, 
             padding = 1)



```

```{r printing plots, echo=FALSE, message=FALSE, warning=FALSE}

print(cor_plots)




```



# Predictive Validity

We assessed the predictive validity of the new DEEP CTN scale (i.e., how
well our measure can predict participant scores on two theoretically
related constructs). The “gold standard” for predictive validity of CTN
measures is how well it predicts pro-environmental behavior (PEB)
(Clayton, 2003; Clayton et al., 2021; Mayer & Frantz, 2004; Tam, 2013).
A zero-order correlation found moderate correlations between PEB and the
new subscales of the DEEP CTN scale.

A linear regression with only the subscales of CTN predicting PEB showed
that Deep, Emotional, and Presence were adequate to predcict PEB, but
not Experiential.

```{r linear regression with only dimensions predicting PEB, echo=FALSE, message=FALSE, warning=FALSE}

dimensions_peb <-
      lm(PEB_Z ~ deep_ctn_z + exp_ctn_z + emo_ctn_z + presc_ctn_z, 
         data = val_data)

dimensions_peb_anova <-
     Anova(dimensions_peb, type = "II")

peb_r2 <-
     calc.relimp(dimensions_peb, type="lmg",
                 rela=F) #setting to T normalizes metrics to sum to 100%

p_vars <- c("deep_ctn_z", "exp_ctn_z", "emo_ctn_z", "presc_ctn_z")
peb_rvalues <- tibble(round(peb_r2$lmg,2)) #partial R2 of all variables
peb_pvalues <- tibble(round(dimensions_peb_anova$`Pr(>F)`,2),
                         .name_repair = "universal") #p values

peb_tot_var<-round(peb_r2$R2, 2) #variance explained by model



#create table of R and P values
R2_peb_table <- 
     bind_cols(p_vars,peb_rvalues, peb_pvalues[-5,]) %>% 
     rename("variable" = `...1`, "Partial R2" = `round(peb_r2$lmg, 2)`, 
            "p" = `round.dimensions_peb_anova..Pr..F....2.`)





#plotting effect sizes
#https://www.mihiretukebede.com/posts/2020-09-30-2020-09-30-plotting-model-coefficients-in-a-forest-plot/
dim_only_output <- broom::tidy(dimensions_peb)
dim_only_conf <- broom::tidy(dimensions_peb, conf.int = T)

model_dim_only <- forestmangr::round_df(dim_only_output, digits = 2)
model_dim_only <- model_dim_only[-1,] #remove the intercept 

coef_dim_only <- 
     coef(dimensions_peb)
ConfidenceInterval_dim_only <- 
     confint(dimensions_peb, level = 0.95)
coef_confint_dim_only <- 
     cbind(coef_dim_only, ConfidenceInterval_dim_only)%>% 
     as.data.frame()
coef_confint_dim_only <- 
     coef_confint_dim_only %>% 
     mutate(variable=rownames(coef_confint_dim_only))


coef_confint_dim_only <- 
     coef_confint_dim_only %>% 
     rename(c("std Beta" = "coef_dim_only",
              "lower_bound" = `2.5 %`, 
              "upper_bound" = `97.5 %`))

# Reorder variables
col_order <- c("variable", "std Beta", "lower_bound", "upper_bound")
coef_confint_dim_only <- 
     coef_confint_dim_only[, col_order] #reorder variables in the data frame

coef_confint_dim_only <- 
     coef_confint_dim_only %>% 
  mutate_if(is.numeric, round, digits = 2) # round numeric into two significant digits 

plot_model_dim_only <- coef_confint_dim_only[-1,] %>%  #remove row number 1 (The intercept) 
  ggplot(aes(x=reorder(variable, `std Beta`), y=`std Beta`)) +
  geom_point(shape = 15,
             size  = 4,
             position = "dodge", 
             color="black") + 
  geom_errorbar(aes(ymin  = lower_bound,
                    ymax  = upper_bound),
                size  = 1,
                position = "dodge", 
                color="turquoise4") +
  theme(axis.title = element_text(face = "bold")) +
  xlab("Variables") + ylab("Beta coeffecients with 95% CI") +
  coord_flip(ylim = c(-.5, .5)) + 
  geom_hline(yintercept = 0, color = "red", size = 1) +
   theme(axis.title = element_text(size = 17)) + 
  theme(axis.text = element_text(size = 14)) 

```

```{r dimonly output, echo=FALSE, message=FALSE, warning=FALSE}


bind_cols(coef_confint_dim_only[-1,], R2_peb_table[,-1]) %>% 
     relocate(c(`Partial R2`, p), .after = variable) %>% 
     flextable() %>% 
     bold(~p < .05, 1:3) %>% 
     bold(~lower_bound > 0, c(1,4,5,6)) %>% 
     footnote(i = 1, j = 4,
              value = as_paragraph("< 0.29 = small; 
                                   0.30-0.49 = medium;
                                   > 0.50 = large"),
              ref_symbols = "*",
              part = "header") %>% 
  autofit()




```

Total variance explained by the model = `r paste(peb_tot_var)`

```{r ploteffectspredict, echo=FALSE, message=FALSE, warning=FALSE}

plot_model_dim_only

```

# Incremental Validity

We explored if the DEEP CTN scale and its facets would perform above and
beyond existing CTN scales (i.e., CNS and EID-R) when predicting PEB. A
linear regression model was run, which included the dimensions of the
DEEP CTN scale and the existing CTN measures (CNS and EIDR) were entered
simultaneously to predict PEB. Note that because overall CTN was highly
intercorrelated with Deep and Emotional, it was left out and only the
four dimensions were included.

We found that the Emotional and Presence subscales remained significant
predictors when existing measures of CTN were entered into the model.
The Deep subscale was no longer a significant predictor. Both our
subscales were of equal predictive value compared to the existing
measures.

```{r predictive validity PEB,include=FALSE, warning=FALSE}

val_data <-
     val_data %>% 
  filter(!is.na(SES_peers_z)) %>% 
     mutate(politics = (politics_overall_Z + politics_economic_z +
                             politics_social_z)/3,
            ses = (SES_family_z + SES_peers_z)/2)

model_peb <- 
     lm(PEB_Z ~ deep_ctn_z + exp_ctn_z + emo_ctn_z + presc_ctn_z +
             CNS_Z + EIDR_Z, data = val_data)

anova_model_peb <-
     Anova(model_peb, type = "II")


incremental_r2 <-
     calc.relimp(model_peb, type="lmg",
                 rela=F) #setting to T normalizes metrics to sum to 100%

incremental_vars <- c("deep_ctn_z", "exp_ctn_z", "emo_ctn_z", "presc_ctn_z", "CTN_Z", "EIDR_Z")
incremental_rvalues <- tibble(round(incremental_r2$lmg,2)) #partial R2 of all variables
incremental_pvalues <- tibble(round(anova_model_peb$`Pr(>F)`,2),
                         .name_repair = "universal") #p values

inc_tot_var <-round(incremental_r2$R2, 2) #variance explained by model



#create table of R and P values
R2_incremental_table <- 
     bind_cols(incremental_vars, incremental_rvalues, incremental_pvalues[-7,]) %>% 
     rename("variable" = `...1`, "Partial R2" = `round(incremental_r2$lmg, 2)`, 
            "p" = `round.anova_model_peb..Pr..F....2.`)







#plotting effect sizes
#https://www.mihiretukebede.com/posts/2020-09-30-2020-09-30-plotting-model-coefficients-in-a-forest-plot/
model_peb_output <- broom::tidy(model_peb)
model_peb_conf <- broom::tidy(model_peb, conf.int = T)

model_peb_out <- forestmangr::round_df(model_peb_conf, digits = 2)
model_peb_out <- model_peb_out[-1,] #remove the intercept 

coef_peb <- 
     coef(model_peb)
ConfidenceInterval_peb <- 
     confint(model_peb, level = 0.95)
coef_confint_peb <- 
     cbind(coef_peb, ConfidenceInterval_peb)%>% 
     as.data.frame()
coef_confint_peb <- 
     coef_confint_peb %>% 
     mutate(variable=rownames(coef_confint_peb))


coef_confint_peb <- 
     coef_confint_peb %>% 
     rename(c("std Beta" = "coef_peb",
              "lower_bound" = `2.5 %`, 
              "upper_bound" = `97.5 %`))

# Reorder variables
col_order <- c("variable", "std Beta", "lower_bound", "upper_bound")
coef_confint_peb <- 
     coef_confint_peb[, col_order] #reorder variables in the data frame

coef_confint_peb <- 
     coef_confint_peb %>% 
  mutate_if(is.numeric, round, digits = 2) # round numeric into two significant digits 

plot_model_peb <- coef_confint_peb[-1,] %>%  #remove row number 1 (The intercept) 
  ggplot(aes(x=reorder(variable, `std Beta`), y=`std Beta`)) +
     geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point(shape = 15,
             size  = 4,
             position = "dodge", 
             color="black") + 
  geom_errorbar(aes(ymin  = lower_bound,
                    ymax  = upper_bound),
                size  = 1,
                position = "dodge", 
                color="turquoise4") +
  theme(axis.title = element_text(face = "bold")) +
  xlab("Variables") + ylab("Beta coeffecients with 95% CI") +
  coord_flip(ylim = c(-.5, .5)) + 
  
   theme(axis.title = element_text(size = 17)) + 
  theme(axis.text = element_text(size = 14)) 
```

```{r model PEB plots, echo=FALSE, warning=FALSE}

bind_cols(coef_confint_peb[-1,], R2_incremental_table[,-1]) %>% 
     relocate(c(`Partial R2`, p), .after = variable) %>% 
     flextable() %>% 
     bold(~p < .05, 1:3) %>% 
     bold(~lower_bound > 0, c(1,4,5,6))%>% 
     footnote(i = 1, j = 4,
              value = as_paragraph("< 0.29 = small; 
                                   0.30-0.49 = medium;
                                   > 0.50 = large"),
              ref_symbols = "*",
              part = "header") %>% 
  autofit()





```

Total variance explained by the model = `r paste(inc_tot_var)`

```{r effectplotincremental, echo=FALSE, message=FALSE, warning=FALSE}
plot_model_peb
```

# Robustness

We also tested the robustness of our new DEEP CTN scale, by testing if
the DEEP CTN scale and its facets are significant predictors of PEB
after controlling for known covariates of these outcomes: political
ideology, gender, and socio-economic status (SES). We fist inspected a
zero order correlation to identify which covariates should be included.
Including any variable that:

1.  strongly correlated with PEB AND

2.  weakly correlated with the Deep CTN Scale may reduce variance in the
    dependent variable and therefore enhance the likelihood of seeing
    significant effects of the DEEP CTN scale.

Further, if an additional variable is…

1.  strongly correlated with BOTH PEB AND

2.  the Deep CTN Scale,

its inclusion in the model will address potential mediating effects
regarding the relationship between the Deep CTN Scale and a DV of
interest. In either case this would suggest it’s important to include as
a covariate.

This resulted in including the following covariates:

-   Politics (r = .19\*\* with PEB & r = .18\*\* to .23\*\* with DEEP
    CTN dimensions)

-   Primal Beliefs - The world is interconnect (r = .21\*\* with PEB & r
    = .22\*\* to .38\*\* with DEEP CTN dimensions)

```{r Robustness Covariates, echo=FALSE, include=FALSE}

val_data <-
  val_data %>% 
  mutate(gender = case_when(gender == "Woman" ~ 0,
                            gender == "Man" ~ 1))


allvarscordata <- 
     val_data %>% 
         dplyr::select(CTN_overall_z,
                 deep_ctn_z,
                 exp_ctn_z,
                 emo_ctn_z,
                 presc_ctn_z,
                 CNS_Z,
                 EIDR_Z,
                 PEB_Z,
                 PI_me_Z,
                 PI_hierarchy_Z,
                 PI_connect_Z,
                 politics,
                 gender, #0 = female, 1=male
                 ses,
                 LOC_Z)  %>% 
          as.matrix()


     

allvarscorrelation <-
     rcorr(allvarscordata, type = "spearman")

allvarscorp <- 
     cor.mtest(allvarscordata)

nm = rownames(allvarscorrelation$r)
m = t(combn(nm, 2))
d = cbind(data.frame(m), R = allvarscorrelation$r[m], P = allvarscorrelation$P[m])
d$label = round(d$R, 2)
d$label[d$P < 0.001] = paste0(d$label[d$P < 0.001], "\n**")
d$X1 = factor(d$X1, nm)
d$X2 = factor(d$X2, rev(nm))

graphics.off()
robustness_plot <- 
  ggplot(d, aes(X1, X2, fill = R, label = label)) +
    geom_tile(color = "white") +
    scale_fill_viridis_c() +
    geom_text(color = ifelse(d$R > 0.35, "black", "white"), size = 2) +
    theme_bw() +
    coord_equal() +
     theme(axis.text.x = element_text(angle = 45, hjust = 1))



```

```{r full zero-order correlation, echo=FALSE}
print(robustness_plot)
```

A multiple linear regression model where dimensions of the DEEP CTN scale and existing CTN measures (CNS and EIDR) and the covariates (politics & primal belief interconnectedness) were entered simultaneously to predict PEB is reported in the table below.


By adding the covariates, both Emotional and Prescence subscales remained significant predictors of PEB


```{r Robustness Existing measures, echo=FALSE, include=FALSE, warning=FALSE}
#dummycode gender
val_data <-
val_data %>% 
     mutate(gender_dummy = as.numeric(gender)) 


robust_model_peb <-
      lm(PEB_Z ~ deep_ctn_z + exp_ctn_z + emo_ctn_z + presc_ctn_z +
             CNS_Z + EIDR_Z + 
             PI_connect_Z + politics, data = val_data)

robust_anova_peb <-
     Anova(robust_model_peb, type = "II")


robust_r2 <-
     calc.relimp(robust_model_peb, type="lmg",
                 rela=F) #setting to T normalizes metrics to sum to 100%

robust_rvalues <- tibble(round(robust_r2$lmg,2)) #partial R2 of all variables
robust_pvalues <- tibble(round(robust_anova_peb$`Pr(>F)`,2),
                         .name_repair = "universal") #p values
vars <- tibble(c("deep_ctn_z", "exp_ctn_z", "emo_ctn_z", "presc_ctn_z", "CTN_Z", "EIDR_Z", "PI_connect_Z", "politics"))

robust_tot_var<- round(robust_r2$R2, 2) #variance explained by model



#create table of R and P values
R2_incremental_peb_robust <- 
     bind_cols(vars, robust_rvalues, robust_pvalues[-9,])%>% 
     rename("variable" = `c(...)`, "Partial R2" = `round(robust_r2$lmg, 2)`, 
            "p" = `round.robust_anova_peb..Pr..F....2.`)
     
#plotting effect sizes
#https://www.mihiretukebede.com/posts/2020-09-30-2020-09-30-plotting-model-coefficients-in-a-forest-plot/
model_robustPEB_output <- broom::tidy(robust_model_peb)
model_robustPEB_conf <- broom::tidy(robust_model_peb, conf.int = T)

model_robustPEB <- forestmangr::round_df(model_robustPEB_conf, digits = 2)
model_robustPEB <- model_robustPEB[-1,] #remove the intercept 

coef_robustPEB <- 
     coef(robust_model_peb)
ConfidenceInterval_robustPEB <- 
     confint(robust_model_peb, level = 0.95)
coef_confint_robustPEB <- 
     cbind(coef_robustPEB, ConfidenceInterval_robustPEB)%>% 
     as.data.frame()
coef_confint_robustPEB <- 
     coef_confint_robustPEB %>% 
     mutate(variable=rownames(coef_confint_robustPEB))


coef_confint_robustPEB <- 
     coef_confint_robustPEB %>% 
     rename(c("std Beta" = "coef_robustPEB",
              "lower_bound" = `2.5 %`, 
              "upper_bound" = `97.5 %`))

# Reorder variables
col_order <- c("variable", "std Beta", "lower_bound", "upper_bound")
coef_confint_robustPEB <- 
     coef_confint_robustPEB[, col_order] #reorder variables in the data frame

coef_confint_robustPEB <- 
     coef_confint_robustPEB %>% 
  mutate_if(is.numeric, round, digits = 2) # round numeric into two significant digits 

plot_model_robustPEB <- coef_confint_robustPEB[-1,] %>%  #remove row number 1 (The intercept) 
  ggplot(aes(x=reorder(variable, `std Beta`), y=`std Beta`)) +
  geom_point(shape = 15,
             size  = 4,
             position = "dodge", 
             color="black") + 
  geom_errorbar(aes(ymin  = lower_bound,
                    ymax  = upper_bound),
                size  = 1,
                position = "dodge", 
                color="turquoise4") +
  theme(axis.title = element_text(face = "bold")) +
  xlab("Variables") + ylab("Beta coeffecients with 95% CI") +
  coord_flip(ylim = c(-.5, .5)) + 
  geom_hline(yintercept = 0, color = "red", size = 1) +
   theme(axis.title = element_text(size = 17)) + 
  theme(axis.text = element_text(size = 14)) 

```

```{r robust PEB output, echo=FALSE, warning=FALSE}


bind_cols(coef_confint_robustPEB[-1,], R2_incremental_peb_robust[,-1]) %>% 
     relocate(c(`Partial R2`, p), .after = variable) %>% 
     flextable() %>% 
     bold(~p < .05, 1:3) %>% 
     bold(~lower_bound > 0, c(1,4,5,6))%>% 
     footnote(i = 1, j = 4,
              value = as_paragraph("< 0.29 = small; 
                                   0.30-0.49 = medium;
                                   > 0.50 = large"),
              ref_symbols = "*",
              part = "header") %>% 
  autofit()







```

Total variance explained by the model = `r paste(robust_tot_var)`

```{r effectplotrobust, echo=FALSE, message=FALSE, warning=FALSE}
plot_model_robustPEB
```

## Comparing Incremental and Robust models

Adding robust variables did not improve the fit of the model above the
variables in the incremental validity model

```{r robust anova table, echo=FALSE, message=FALSE, warning=FALSE}
#Compare models

model_names <- c("Incremental", "Robust")

comparison <-
anova(model_peb, robust_model_peb)

bind_cols(model_names, comparison) %>% 
  flextable() %>% 
  autofit()
```
