---
title: 'DEEP CTN CFA (Pilot 1 SONA Spr23)'
author: Deb Lindsay
date: "`r Sys.Date()`"
slug: CFA_sp23
categories: 
  - CFA
tags:
  - Connection to Nature
  - Paper 1
  - DEEP CTN
subtitle: ''
summary: ''
authors: []
lastmod: "`r Sys.Date()`"
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
output:
  blogdown::html_page:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

```{r Packages and Functions required, include=FALSE}

library(tidyverse) #base package that runs most functions
library(flextable) #tables
library(moments) #skewness & kurtosis
library(lavaan) #CFA 
library(corrplot) #correlations
library(MVN) #test of normality
library(semPlot) #plotting paths in CFA
library(Hmisc) #correlations 
library(car) # Type 2 Anova
library(effectsize) #effect sizes
library(ggplot2) #plots
```

```{r loading data, include=FALSE}
CFA1 <- 
     read_csv("CFApilot1SONA_data_clean.csv")

```

Pilot data collected during the Spring quarter (2023) on SONA students. This was piloting the CFA that will be run on Prolific participants Jan 2024.

# Sample Descriptives {.tabset}

```{r Means, include=TRUE, echo=FALSE,}

n <- paste(round((length(CFA1$id)), 2))
     
m_age <- paste(round(mean(CFA1$age, na.rm = T),2))
sd_age <- paste(round(sd(CFA1$age, na.rm = T),2))
min_age <- min(CFA1$age, na.rm = T)
max_age <- max(CFA1$age, na.rm = T)

m_ses <- paste(round(mean(CFA1$SES_family, na.rm = T),2))
sd_ses <- paste(round(sd(CFA1$SES_family, na.rm = T),2))

m_pol <- paste(round(mean(CFA1$politics_overall, na.rm = T),2))
sd_pol <- paste(round(sd(CFA1$politics_overall, na.rm = T),2))
```

Total sample size was N = `r paste(n)` . The mean age of sample was `r paste(m_age)`(`r paste(sd_age)`). Age range: `r paste(min_age)` - `r paste(max_age)`

```{r agegraph, echo=FALSE, message=FALSE, warning=FALSE}

CFA1 %>% 
  ggplot() +
  geom_histogram(aes(age)) +
  theme_minimal()

```

Family SES was scored on a 10-point ladder,with 10 being the best off, and 1 being the worst off. The mean SES was `r paste(m_ses)`(`r paste(sd_ses)`).

```{r sesgraph, echo=FALSE, message=FALSE, warning=FALSE}

CFA1 %>% 
  ggplot() +
  geom_histogram(aes(SES_family)) +
  scale_x_continuous(breaks = c(1:10)) +
  theme_minimal()

```

Political Ideology was scored on a 7-point Likert scale with 1 = Most Conservative and 7 = Most Liberal. The mean political ideology was `r paste(m_pol)`(`r paste(sd_pol)`), showing that this sample skewed more liberal. This is to be expected with our student sample.\

```{r polgraph, echo=FALSE, message=FALSE, warning=FALSE}

CFA1 %>% 
  ggplot() +
  geom_histogram(aes(politics_overall)) +
  scale_x_continuous(breaks = c(1:7)) +
  theme_minimal()

```

Gender and ethnoracial demographics are reported in the tables below.

```{r gender table, include=FALSE}
desc_table <-
CFA1 %>% 
     group_by(gender) %>% 
     summarise(n = length(id),
               `Age(mean)` = round(mean(age, na.rm = T),2),
              `Age(sd)` = ifelse(is.na(sd(age, na.rm=T)), print(NaN), print(round(sd(age, na.rm = T),2)))) 



```

::: row
::: {.col-xs-12 .col-md-6}
```{r printdesctable, echo=FALSE, message=FALSE, paged.print=FALSE}
 
     flextable(desc_table) %>% 
  autofit() 
     #%>% 
 # set_caption(caption = "Gender")

```

`r officer::run_columnbreak()`
:::

::: {.col-xs-12 .col-md-6}
```{r race, echo=FALSE}
CFA1 %>% 
     group_by(ethnoracial) %>% 
     summarise(n = length(id)) %>% 
     flextable() %>% 
  autofit() #%>% 
 # set_caption(caption = "Ethnoracial")

```
:::
:::

<!---BLOCK_MULTICOL_STOP{widths: [4,2], space: 0.1, sep: false}--->

```{r factor data frame, include=FALSE}

#pull out non-binary participants as the n is not big enough to run analyses
#removed 9 participants
CFA1 <-    
 CFA1 %>% 
     filter(gender == "Woman" | gender == "Man") 

factors <- 
     CFA1 %>% 
     dplyr::select(DEEPCTN_s_1:DEEPCTN_em_6)

```

------------------------------------------------------------------------

# CFA Assumptions

## Skewness & Kurtosis

The closer to 0 for skewness and kurtosis, the closer to a normal distribution. Based on the general guidelines below - Distributions exhibiting skewness and/or kurtosis that exceed these guidelines are considered non-normal." (Hair et al., 2017, p. 61, [Statology Link](https://urldefense.com/v3/__https://www.statology.org/skewness-kurtosis-in-r/__;!!Mih3wA!AZTiIebL9bHjEkMldcV0F-RHoO1rmMMzVCj9u0soFHPUcRstrVs69kjeDTvnGWiLF9ZkmFYq16GWFhwP6w$)).

### **Skewness**

Ff the number is greater than +1 (right skewed) or lower than --1 (left skewed), this is an indication of a substantially skewed distribution.

::: {style="color:blue"}
*No items with high skewness*
:::

```{r Skewness, include=TRUE, echo=FALSE}
skew <-as.data.frame(round(sort(skewness(factors),
     decreasing = T),2))
```

### **Kurtosis**

If the number is greater than +3, the distribution is too peaked. Likewise, a kurtosis of less than --3 indicates a distribution that is too flat.

::: {style="color:blue"}
*Three items with slightly high Kurtosis:*

1.  DEEPCTN_s_5\
    "**I have great respect for being alive on this earth and part of the universe"**

2.  DEEPCTN_ex_7\
    "**Listening to the sounds of nature makes me relax"**

3.  DEEPCTN_em_5\
    "**I am careful to not step on snails"**
:::

```{r Kurtosis, include=TRUE, echo=FALSE}
kurtosis <- as.data.frame(round(sort(kurtosis(factors),
     decreasing=T),2))
```

```{r Historgrams, include=FALSE, results='hide', eval=FALSE}

# Deep
factors %>% 
     ggplot(aes(DEEPCTN_s_1)) +
     geom_histogram() +
     scale_x_continuous(breaks = c(1:7))

factors %>% 
     ggplot(aes(DEEPCTN_s_2)) +
     geom_histogram() +
     scale_x_continuous(breaks = c(1:7))

factors %>% 
     ggplot(aes(DEEPCTN_s_3)) +
     geom_histogram() +
     scale_x_continuous(breaks = c(1:7))

factors %>% 
     ggplot(aes(DEEPCTN_s_4)) +
     geom_histogram() +
     scale_x_continuous(breaks = c(1:7))

factors %>% 
     ggplot(aes(DEEPCTN_s_5)) +
     geom_histogram() +
     scale_x_continuous(breaks = c(1:7))

factors %>% 
     ggplot(aes(DEEPCTN_s_7)) +
     geom_histogram() +
     scale_x_continuous(breaks = c(1:7))

factors %>% 
     ggplot(aes(DEEPCTN_s_8)) +
     geom_histogram() +
     scale_x_continuous(breaks = c(1:7))

factors %>% 
     ggplot(aes(DEEPCTN_s_9)) +
     geom_histogram() +
     scale_x_continuous(breaks = c(1:7))

factors %>% 
     ggplot(aes(DEEPCTN_s_10)) +
     geom_histogram() +
     scale_x_continuous(breaks = c(1:7))

# Experience
factors %>% 
     ggplot(aes(DEEPCTN_ex_1)) +
     geom_histogram() +
     scale_x_continuous(breaks = c(1:7))

factors %>% 
     ggplot(aes(DEEPCTN_ex_2)) +
     geom_histogram() +
     scale_x_continuous(breaks = c(1:7))

factors %>% 
     ggplot(aes(DEEPCTN_ex_3)) +
     geom_histogram() +
     scale_x_continuous(breaks = c(1:7))

factors %>% 
     ggplot(aes(DEEPCTN_ex_4)) +
     geom_histogram() +
     scale_x_continuous(breaks = c(1:7))

factors %>% 
     ggplot(aes(DEEPCTN_ex_5)) +
     geom_histogram() +
     scale_x_continuous(breaks = c(1:7))

factors %>% 
     ggplot(aes(DEEPCTN_ex_6)) +
     geom_histogram() +
     scale_x_continuous(breaks = c(1:7))

factors %>% 
     ggplot(aes(DEEPCTN_ex_7)) +
     geom_histogram() +
     scale_x_continuous(breaks = c(1:7))

factors %>% 
     ggplot(aes(DEEPCTN_ex_8)) +
     geom_histogram() +
     scale_x_continuous(breaks = c(1:7))

# Emotion
factors %>% 
     ggplot(aes(DEEPCTN_emo_1)) +
     geom_histogram() +
     scale_x_continuous(breaks = c(1:7))

factors %>% 
     ggplot(aes(DEEPCTN_emo_2)) +
     geom_histogram() +
     scale_x_continuous(breaks = c(1:7))

factors %>% 
     ggplot(aes(DEEPCTN_emo_3)) +
     geom_histogram() +
     scale_x_continuous(breaks = c(1:7))

factors %>% 
     ggplot(aes(DEEPCTN_emo_4)) +
     geom_histogram() +
     scale_x_continuous(breaks = c(1:7))

factors %>% 
     ggplot(aes(DEEPCTN_em_5)) +
     geom_histogram() +
     scale_x_continuous(breaks = c(1:7))

factors %>% 
     ggplot(aes(DEEPCTN_em_6)) +
     geom_histogram() +
     scale_x_continuous(breaks = c(1:7))

# Presence
factors %>% 
     ggplot(aes(DEEPCTN_m_1)) +
     geom_histogram() +
     scale_x_continuous(breaks = c(1:7))

factors %>% 
     ggplot(aes(DEEPCTN_m_2)) +
     geom_histogram() +
     scale_x_continuous(breaks = c(1:7))

factors %>% 
     ggplot(aes(DEEPCTN_m_3)) +
     geom_histogram() +
     scale_x_continuous(breaks = c(1:7))

factors %>% 
     ggplot(aes(DEEPCTN_m_4)) +
     geom_histogram() +
     scale_x_continuous(breaks = c(1:7))

factors %>% 
     ggplot(aes(DEEPCTN_m_5)) +
     geom_histogram() +
     scale_x_continuous(breaks = c(1:7))

factors %>% 
     ggplot(aes(DEEPCTN_m_6)) +
     geom_histogram() +
     scale_x_continuous(breaks = c(1:7))
```

## Inter-item Correlation

::: {style="color: blue"}
*None are strongly ( \>.75) correlated so no need to remove any*
:::

```{r Correlation Matrix, echo=FALSE, out.width="100%"}
#see if any item is too strongly correlated

corrplot(cor(factors),
         method="shade",
         type="upper",
         order="original",
         addCoef.col = "black",
         tl.col="black", 
         tl.srt=55, 
         tl.cex=.65,
         sig.level = 0.05, 
         insig = "blank",
         number.cex = .35,
         cl.pos = "n") 

```

```{r Correlations Large, include=FALSE}
#pull out too strong ones
factors %>% 
    select_if(is.numeric) %>%
    cor() %>% 
    round(digits = 2) %>%
    as.data.frame() %>%
    rownames_to_column %>%
    gather(colname, value, -rowname) %>%
    group_by(rowname) %>%
  filter(abs(value) >= 0.75) %>%
  filter(abs(value) != 1)
```

## Multivariate normality

#### Notes on Multivariate Normality

-   Quantiative test of normality: shapiro is fine for univariate normality test. But I also need to test for multivariate normality. This package is both. Use this.
-   Can just look at univariate for now, but REPEAT THIS with my final variables to check for multivariate normality
-   Sources:
    -   [Lavaan Package notes](https://shiny.rit.albany.edu/stat/cfa1test/data.html)
    -   [MVN Package Notes](https://cran.r-project.org/web/packages/MVN/MVN.pdf)
    -   [How to perform multivariate normality tests in R](https://www.statology.org/multivariate-normality-test-r/)
    -   [How to transform data in R](https://www.statology.org/transform-data-in-r/)

::: {style="color: blue"}
*Using the Mardia Test of multivariate AND univariate normality. Mardia test shows that my data is [**not normal**]{.underline}. This indicates that I need to use a rotation method that is robust to non-normal data.*
:::

```{r Mardia Test, echo=FALSE}
#this tells you multivariate normality of all the items AND univariate normality of each item
norm_result <- mvn(data= factors, 
    mvnTest="mardia",  
    univariateTest="SW",  #shaprio-wilkes
    # transform="log", #what are results if you transform all variables like this?
    # univariatePlot = "histogram",
    # multivariatePlot = "qq"
    )

```

##### Multivariate Normality

```{r Mardia multivariate, results=TRUE, echo=FALSE}
print(norm_result$multivariateNormality)

```

##### Univariate Normality

```{r Mardia Univariate, results=TRUE, echo=FALSE}
print(norm_result$univariateNormality)
print(norm_result$Descriptives)

```

##### Norm Descriptives for each item

```{r Mardia Norm Descriptives, results=TRUE, echo=FALSE}
print(norm_result$univariateNormality)

```

## CFA Preparation

::: {style="color: blue"}
*Only items that were decided upon during EFA pilots to be concluded*

*Remove items with too heavy kurtosis (see above)*

*All analyses going forward will only include the following items:*
:::

```{r remove high kurtosis, include=FALSE}

final_factors <-
     factors %>% 
     dplyr::select(DEEPCTN_s_1,
            DEEPCTN_s_2,
            DEEPCTN_s_3,
            DEEPCTN_s_7,
            DEEPCTN_s_10,
            DEEPCTN_s_8, 
            DEEPCTN_s_4,
            DEEPCTN_s_6, 
            DEEPCTN_s_9,
            DEEPCTN_ex_4,
            DEEPCTN_ex_5,
            DEEPCTN_ex_6,
            DEEPCTN_ex_8,
            DEEPCTN_ex_1, 
            DEEPCTN_ex_2,
            DEEPCTN_ex_3,
            DEEPCTN_m_1,
            DEEPCTN_m_2,
            DEEPCTN_m_3,
            DEEPCTN_m_4,
            DEEPCTN_m_5,
            DEEPCTN_m_6,
            DEEPCTN_emo_1,
            DEEPCTN_emo_2,
            DEEPCTN_emo_3,
            DEEPCTN_emo_4,
            DEEPCTN_em_6)

```

```{r variables names, include=FALSE, echo=FALSE}

Items <-
  c("I view nature as a mother who nurtures and cares for me",
    "Human beings and nature are connected by the same *energy* or *Life-force*",
    "My connection to nature is something I would describe as *spiritual*",
    "I think about the *shared breath* between myself and plants; I breathe in the oxygen released by plants, and plants use the carbon dioxide I exhale",
    "When I eat, I feel thankful for the animals, plants, and earth for nourishing me",
    "I often think about the fact that all life is grounded on this planet that is revolving around the sun",
    "Every part of nature is sacred",
    "I like the idea that, when I die, my body will return to the earth, nourishing the soil",
    "Indoor plants are part of the family",
    "My favorite place is in nature",
    "Walking through a forest makes me forget about my daily worries",
    "I prefer outdoor to indoor sports",
    "I hike or run in nearby nature",
    "I like to get outdoors whenever I get the chance",
    "I feel uneasy if I am away from nature for too long",
    "I engage and participate with nature to find meaning and richness in life",
    "I take time to watch the clouds pass by",
    "I deliberately take time to watch stars at night",
    "When possible I take time to watch the sunrise or the sunset without distractions",
    "I consciously watch or listen to birds",
    "I take time to consciously smell flowers",
    "I pay attention to the current phase of the moon",
    "Seeing a cleared forest is upsetting to me",
    "If one of my plants died, I would blame myself",
    "Thinking of someone carving their initials into a tree makes me cringe",
    "If there is an insect, such as a fly or a spider, in my home, I try to catch and release it rather than kill it",
    "I talk to the wild animals I encounter (e.g., birds, lizards, rabbits, squirrels)")

final_items <- data_frame(variable.names(final_factors), Items) %>% 
     print(n = Inf) %>% 
     rename(Code  = `variable.names(final_factors)`)

```

```{r Final Items, echo=FALSE, warning=FALSE}

flextable(final_items) %>% 
     set_table_properties(layout = "autofit") %>% 
  autofit()


```

##  {.unlisted .unnumbered}

------------------------------------------------------------------------

# CFA {.tabset .tabset-fade}

## Four Factor Hierarchical Model

Testing a structure which includes an overall Connection to Nature factor and four dimensions:

-   Deep: Deeply seeing the self as part of nature

-   Experiential: Spending more time in nature and enjoying spending time in nature

-   Emotional: Emotional desire to connect with nature and protect it

-   Presence: Engaging mindfully and consciously with nature

::: {style="color: blue"}
*Items load onto their dimensions well, with the exception of 1 item ("Thinking of someone carving their initials into a tree makes me cringe") which loaded onto the Emotion dimension at 0.33.*

*All dimensions loaded onto the single CTN dimension, but these loaded quite highly (especially Deep and Emotion) which suggests these might be driving the overall CTN score.*
:::

```{r CFA - 4 factor hierarchical, echo=FALSE, include=FALSE}
model_hier_4 <-  'deep =~ 
  DEEPCTN_s_1 + 
  DEEPCTN_s_2 +
  DEEPCTN_s_3 +
  DEEPCTN_s_7 +
  DEEPCTN_s_10 +
  DEEPCTN_s_8 +
  DEEPCTN_s_4 +
  DEEPCTN_s_6 +
  DEEPCTN_s_9

experience =~ 
   DEEPCTN_ex_4 +
   DEEPCTN_ex_5 +
   DEEPCTN_ex_6 +
   DEEPCTN_ex_8 +
   DEEPCTN_ex_1 +
   DEEPCTN_ex_2 +
   DEEPCTN_ex_3

emotion =~ 
  DEEPCTN_emo_1 +
  DEEPCTN_emo_2 +
  DEEPCTN_emo_3 +
  DEEPCTN_emo_4 +
  DEEPCTN_em_6

presence =~
  DEEPCTN_m_1 +
  DEEPCTN_m_2 +
  DEEPCTN_m_3 +
  DEEPCTN_m_4 +
  DEEPCTN_m_5 +
  DEEPCTN_m_6


deepctn =~ deep + experience + emotion + presence'

fit_model_hier_4 <- cfa(model_hier_4, data=final_factors,
                        std.lv=F, #set to T to get Std.Err!!!
                        estimator = "MLR") #robust against non normal data #https://lavaan.ugent.be/tutorial/est.html



Plot <-
     semPaths(fit_model_hier_4, 
         whatLabels = "std", #"par" = unstandardized loading, "std" = standardized. In graphs std is more common. Here the top variable error variance goes to 1 because everything is standardized on that latent variable. This also standarizes all the errors which makes them SD's
        layout="tree",
        rotation = 4,
        weighted = T, #makes lines bolder for higher numbers
        nCharNodes = 10, #number of text characters to allow in each box
        shapeMan = "rectangle", 
        sizeMan = 35, 
        sizeMan2 = 2,
        border.width = .5,
        label.prop = 0.8,
        asize = 1.5,
        mar = c(.5,5,.5,4),
        residuals=F, #errors? how do I interpret this?
        curvePivot = TRUE, 
        edge.label.cex= .75, #size of numbers
        cardinal = TRUE,
        nodeLabels = c("View nature as a mother", #Deep
                       "Humans and nature connected by same 'Energy'", 
                       "My connection is 'Spiritual'", 
                       "'Shared breath' between myself and plants", 
                       "When I eat, I feel thankful for animals and plants",
                       "All life is grounded on this planet", 
                       "Every part of nature is sacred",
                       "When I die, my body will return to the earth", 
                       "Indoor plants are family",
                       "My favorite is in nature", #experience 
                       "Walking through a forest makes me forget worries", 
                       "I prefer outdoor sports", 
                       "I hike or run in nearby nature", 
                       "I like to get outdoors when I can", 
                       "I feel uneasy if away from nature for too long", 
                       "I engage in nature to find meaning & richness",
                       "Seeing a cleared forest is upsetting", #emotional
                       "If my plants died I would blame myself", 
                       "Someone carving a tree makes me cringe", 
                       "I catch and release insects in my home", 
                       "I talk to wild animals I encounter",
                       "I take time to watch the clouds pass by", #prescence
                       "I deliberately watch the Stars at night", 
                       "I take time to watch the sunrise & sunset", 
                       "I consciously listen to birds", 
                       "I take time to consciously smell flowers", 
                       "I pay attention to phases of the moon",
                       "Deep", 
                       "Experience", 
                       "Emotion", 
                       "Presence",
                       "Overall CTN")
        )

Fit_table_heir <- matrix(fitMeasures(fit_model_hier_4, c("df", "chisq", "rmsea", "rmsea.ci.lower", "rmsea.ci.upper", "srmr", "tli", "cfi", "aic")), 
                         ncol=9,
                         byrow=TRUE)

colnames(Fit_table_heir) <- c("df", "Chi-Sq", "RMSEA","RMSEA CI Lower", "RMSEA CI Upper", "SRMR", "TLI", "CFI", "AIC")
rownames(Fit_table_heir) <- c("Fit Indices")
Fit_table_heir <- round(Fit_table_heir,3)


```

```{r 4 factor hierarchical plot, include=TRUE, echo=FALSE, out.width="100%"}
plot(Plot)

as_tibble(Fit_table_heir) %>% 
  add_column(c(""), .before = "df") %>%
      rename(`Fit Indices` = `c("")`) %>% 
     flextable() %>% 
     autofit() %>% 
     footnote(i = 1, j = 3:4, 
              value = as_paragraph(c("Closer to 0 indicate better fit",
                        "(Root mean square error) 0.01 = Excellent; 0.05 = Good; 0.08 = Mediocre")),
              ref_symbols = c("a", "b"),
              part = "header",
              inline = FALSE) %>% 
     footnote(i = 1, j = 7:10,
              value = as_paragraph(c("(Standardized root mean square residual) Closer to 0 indicate better fit",
                        "(Tucker Lewis Index) Closer to 1 indicates better fit",
                        "(Comparative fit index) Closer to 1 indicates better fit",
                        "(Akaike’s Information Criterion) The lower the AIC, the more predictive")),
              ref_symbols = c("c", "d", "e", "f"),
              part = "header",
              inline = FALSE)
     

#summary(fit_model_hier_4, 
#        standardized = T,
#        fit.measures = T,
#        rsquare=T)
```

## Four Factor Model

Testing a structure which only includes the four dimensions:

-   Deep: Deeply seeing the self as part of nature

-   Experiential: Spending more time in nature and enjoying spending time in nature

-   Emotional: Emotional desire to connect with nature and protect it

-   Presence: Engaging mindfully and consciously with nature

::: {style="color: blue"}
*Items load onto their dimensions similarly well to the hierarchical model. Again, 1 item loads weakly: ("Thinking of someone carving their initials into a tree makes me cringe") which loaded onto the Emotion dimension at 0.33.*

*Dimensions are intercorrelated reasonable well - not too high as to have multi-collinearity (none above .80)*
:::

```{r 4 Factor flat, include=FALSE, echo=FALSE}
model_flat_4 <-  'deep =~ 
  DEEPCTN_s_1 + 
  DEEPCTN_s_2 +
  DEEPCTN_s_3 +
  DEEPCTN_s_7 +
  DEEPCTN_s_10 +
  DEEPCTN_s_8 +
  DEEPCTN_s_4 +
  DEEPCTN_s_6 +
  DEEPCTN_s_9

experience =~ 
   DEEPCTN_ex_4 +
   DEEPCTN_ex_5 +
   DEEPCTN_ex_6 +
   DEEPCTN_ex_8 +
   DEEPCTN_ex_1 +
   DEEPCTN_ex_2 +
   DEEPCTN_ex_3

emotion =~ 
  DEEPCTN_emo_1 +
  DEEPCTN_emo_2 +
  DEEPCTN_emo_3 +
  DEEPCTN_emo_4 +
  DEEPCTN_em_6

presence =~
  DEEPCTN_m_1 +
  DEEPCTN_m_2 +
  DEEPCTN_m_3 +
  DEEPCTN_m_4 +
  DEEPCTN_m_5 +
  DEEPCTN_m_6'
fit_model_flat_4 <- cfa(model_flat_4, data=final_factors,
                        std.lv=F, #set to T to get Std.Err!!!
                        estimator = "MLR") #robust against non normal data #https://urldefense.com/v3/__https://lavaan.ugent.be/tutorial/est.html__;!!Mih3wA!AZTiIebL9bHjEkMldcV0F-RHoO1rmMMzVCj9u0soFHPUcRstrVs69kjeDTvnGWiLF9ZkmFYq16Hy0Ekyig$ 




Plot_4_flat <-
     semPaths(fit_model_flat_4, 
         whatLabels = "std", #"par" = unstandardized loading, "std" = standardized. In graphs std is more common. Here the top variable error variance goes to 1 because everything is standardized on that latent variable. This also standarizes all the errors which makes them SD's
        layout="tree",
        rotation = 4,
        weighted = T, #makes lines bolder for higher numbers
        nCharNodes = 10, #number of text characters to allow in each box
        shapeMan = "rectangle", 
        sizeMan = 35, 
        sizeMan2 = 2,
        border.width = .5,
        label.prop = 0.8,
        asize = 1.5,
        mar = c(.5,5,.5,4),
        residuals=F, #errors? how do I interpret this?
        curvePivot = TRUE, 
        edge.label.cex=.75, #size of numbers
        cardinal = TRUE,
        nodeLabels = c("View nature as a mother", #Deep
                       "Humans and nature connected by same 'Energy'", 
                       "My connection is 'Spiritual'", 
                       "'Shared breath' between myself and plants", 
                       "When I eat, I feel thankful for animals and plants",
                       "All life is grounded on this planet", 
                       "Every part of nature is sacred",
                       "When I die, my body will return to the earth", 
                       "Indoor plants are family",
                       "My favorite is in nature", #experience 
                       "Walking through a forest makes me forget worries", 
                       "I prefer outdoor sports", 
                       "I hike or run in nearby nature", 
                       "I like to get outdoors when I can", 
                       "I feel uneasy if away from nature for too long", 
                       "I engage in nature to find meaning & richness",
                       "Seeing a cleared forest is upsetting", #emotional
                       "If my plants died I would blame myself", 
                       "Someone carving a tree makes me cringe", 
                       "I catch and release insects in my home", 
                       "I talk to wild animals I encounter",
                       "I take time to watch the clouds pass by", #presence
                       "I deliberately watch the Stars at night", 
                       "I take time to watch the sunrise & sunset", 
                       "I consciously listen to birds", 
                       "I take time to consciously smell flowers", 
                       "I pay attention to phases of the moon",
                       "Deep", 
                       "Experience", 
                       "Emotion", 
                       "Presence")
        )


Fit_table_4factor <- matrix(fitMeasures(fit_model_flat_4, c("df", "chisq", "rmsea", "rmsea.ci.lower", "rmsea.ci.upper", "srmr", "tli", "cfi", "aic")), 
                         ncol=9,
                         byrow=TRUE)

colnames(Fit_table_4factor) <- c("df", "Chi-Sq", "RMSEA","RMSEA CI Lower", "RMSEA CI Upper", "SRMR", "TLI", "CFI", "AIC")
rownames(Fit_table_4factor) <- c("Fit Indices")
Fit_table_4factor <- round(Fit_table_4factor,3)



```

```{r flat 4 factor model plot, echo=FALSE, out.width="100%"}
plot(Plot_4_flat)


as_tibble(Fit_table_4factor) %>% 
  add_column(c(""), .before = "df") %>%
      rename(`Fit Indices` = `c("")`) %>% 
     flextable() %>% 
     autofit() %>% 
     footnote(i = 1, j = 3:4, 
              value = as_paragraph(c("Closer to 0 indicate better fit",
                        "(Root mean square error) 0.01 = Excellent; 0.05 = Good; 0.08 = Mediocre")),
              ref_symbols = c("a", "b"),
              part = "header",
              inline = FALSE) %>% 
     footnote(i = 1, j = 7:10,
              value = as_paragraph(c("(Standardized root mean square residual) Closer to 0 indicate better fit",
                        "(Tucker Lewis Index) Closer to 1 indicates better fit",
                        "(Comparative fit index) Closer to 1 indicates better fit",
                        "(Akaike’s Information Criterion) The lower the AIC, the more predictive")),
              ref_symbols = c("c", "d", "e", "f"),
              part = "header",
              inline = FALSE)



#summary(fit_model_flat_4, 
#        standardized = T,
#        fit.measures = T,
#        rsquare=T) 

```

## Single Factor Model

Testing a structure which includes only a single overall Connection to Nature factor

::: {style="color: blue"}
*Loadings are slightly weaker onto a single overall CTN factor. Again, 1 item loads weakly: ("Thinking of someone carving their initials into a tree makes me cringe") which loaded onto the Emotion dimension at 0.31.*
:::

```{r CFA - 1 factor, include=FALSE, echo=FALSE}

model_flat <-  'overall =~ 
  DEEPCTN_s_1 + 
  DEEPCTN_s_2 +
  DEEPCTN_s_3 +
  DEEPCTN_s_7 +
  DEEPCTN_s_10 +
  DEEPCTN_s_8 +
  DEEPCTN_s_4 +
  DEEPCTN_s_6 +
  DEEPCTN_s_9 +

   DEEPCTN_ex_4 +
   DEEPCTN_ex_5 +
   DEEPCTN_ex_6 +
   DEEPCTN_ex_8 +
   DEEPCTN_ex_1 +
   DEEPCTN_ex_2 +
   DEEPCTN_ex_3 +

  DEEPCTN_emo_1 +
  DEEPCTN_emo_2 +
  DEEPCTN_emo_3 +
  DEEPCTN_emo_4 +
  DEEPCTN_em_6 +

  DEEPCTN_m_1 +
  DEEPCTN_m_2 +
  DEEPCTN_m_3 +
  DEEPCTN_m_4 +
  DEEPCTN_m_5 +
  DEEPCTN_m_6'

fit_model_flat <- cfa(model_flat, data=final_factors,
                        std.lv=F, #set to T to get Std.Err!!!
                        estimator = "MLR") #robust against non normal data #https://urldefense.com/v3/__https://lavaan.ugent.be/tutorial/est.html__;!!Mih3wA!AZTiIebL9bHjEkMldcV0F-RHoO1rmMMzVCj9u0soFHPUcRstrVs69kjeDTvnGWiLF9ZkmFYq16Hy0Ekyig$ 



Plot_1 <-
     semPaths(fit_model_flat, 
         whatLabels = "std", #"par" = unstandardized loading, "std" = standardized. In graphs std is more common. Here the top variable error variance goes to 1 because everything is standardized on that latent variable. This also standarizes all the errors which makes them SD's
        layout="tree",
        rotation = 4,
        weighted = T, #makes lines bolder for higher numbers
        nCharNodes = 10, #number of text characters to allow in each box
        shapeMan = "rectangle", 
        sizeMan = 35, 
        sizeMan2 = 2,
        border.width = .5,
        label.prop = 0.8,
        asize = 1.5,
        mar = c(.5,5,.5,4),
        residuals=F, #errors? how do I interpret this?
        curvePivot = TRUE, 
        edge.label.cex=.75, #size of numbers
        cardinal = TRUE,
        nodeLabels = c("View nature as a mother", #Deep
                       "Humans and nature connected by same 'Energy'", 
                       "My connection is 'Spiritual'", 
                       "'Shared breath' between myself and plants", 
                       "When I eat, I feel thankful for animals and plants",
                       "All life is grounded on this planet", 
                       "Every part of nature is sacred",
                       "When I die, my body will return to the earth", 
                       "Indoor plants are family",
                       "My favorite is in nature", #experience 
                       "Walking through a forest makes me forget worries", 
                       "I prefer outdoor sports", 
                       "I hike or run in nearby nature", 
                       "I like to get outdoors when I can", 
                       "I feel uneasy if away from nature for too long", 
                       "I engage in nature to find meaning & richness",
                       "Seeing a cleared forest is upsetting", #emotional
                       "If my plants died I would blame myself", 
                       "Someone carving a tree makes me cringe", 
                       "I catch and release insects in my home", 
                       "I talk to wild animals I encounter",
                       "I take time to watch the clouds pass by", #prescence
                       "I deliberately watch the Stars at night", 
                       "I take time to watch the sunrise & sunset", 
                       "I consciously listen to birds", 
                       "I take time to consciously smell flowers", 
                       "I pay attention to phases of the moon",
                      "CTN Overall"))


Fit_table_flat <- matrix(fitMeasures(fit_model_flat, c("df", "chisq", "rmsea", "rmsea.ci.lower", "rmsea.ci.upper", "srmr", "tli", "cfi", "aic")), 
                         ncol=9,
                         byrow=TRUE)

colnames(Fit_table_flat) <- c("df", "Chi-Sq", "RMSEA","RMSEA CI Lower", "RMSEA CI Upper", "SRMR", "TLI", "CFI", "AIC")
rownames(Fit_table_flat) <- c("Fit Indices")
Fit_table_flat <- round(Fit_table_flat,3)

```

```{r single factor plot, echo=FALSE, out.width="100%"}


plot(Plot_1)


as_tibble(Fit_table_flat) %>% 
  add_column(c(""), .before = "df") %>%
      rename(`Fit Indices` = `c("")`) %>% 
     flextable() %>% 
     autofit() %>% 
     footnote(i = 1, j = 3:4, 
              value = as_paragraph(c("Closer to 0 indicate better fit",
                        "(Root mean square error) 0.01 = Excellent; 0.05 = Good; 0.08 = Mediocre")),
              ref_symbols = c("a", "b"),
              part = "header",
              inline = FALSE) %>% 
     footnote(i = 1, j = 7:10,
              value = as_paragraph(c("(Standardized root mean square residual) Closer to 0 indicate better fit",
                        "(Tucker Lewis Index) Closer to 1 indicates better fit",
                        "(Comparative fit index) Closer to 1 indicates better fit",
                        "(Akaike’s Information Criterion) The lower the AIC, the more predictive")),
              ref_symbols = c("c", "d", "e", "f"),
              part = "header",
              inline = FALSE)

#summary(fit_model_flat, 
#        standardized = T,
#        fit.measures = T,
#        rsquare=T) 

```

## Comparing Fit of each Model

Comparing the fit of the three models

[*Sources for fit indices*](https://en.wikipedia.org/wiki/Confirmatory_factor_analysis)

::: {style="color: blue"}
*Both four-factor models (flat and hierarchical) perform better than the single-factor model.*

*There is no difference between the hierarchical and the flat models.*
:::

```{r fit measures, echo=FALSE}
#cutoffs:
# fit_model_flat
# fit_model_hier_4
# fit_mode_flat_4


 #(RMSEA + CI), (SRMR), (TFI), (CFI) , (AIC)
# df4, chi-sq3, RMSEA47, RMSEACIL48, RMSEACIU49, SRMR67, TLI18, CFI17, AIC37
# df, chisq, rmsea, rmsea.ci.lower, rmsea.ci.upper, srmr, tli cfi, aic
# include the AIC and the confidence interval 


Fit_table <- matrix(c(
                  fitmeasures(fit_model_flat, "df"),
                  fitmeasures(fit_model_flat, "chisq"),
                  fitmeasures(fit_model_flat, "rmsea"),
                  fitmeasures(fit_model_flat, "rmsea.ci.lower"),
                  fitmeasures(fit_model_flat, "rmsea.ci.upper"),
                  fitmeasures(fit_model_flat, "srmr"),
                  fitmeasures(fit_model_flat, "tli"),
                  fitmeasures(fit_model_flat, "cfi"),
                  fitmeasures(fit_model_flat, "aic"),
                  
                  fitmeasures(fit_model_flat_4, "df"),
                  fitmeasures(fit_model_flat_4, "chisq"),
                  fitmeasures(fit_model_flat_4, "rmsea"),
                  fitmeasures(fit_model_flat_4, "rmsea.ci.lower"),
                  fitmeasures(fit_model_flat_4, "rmsea.ci.upper"),
                  fitmeasures(fit_model_flat_4, "srmr"),
                  fitmeasures(fit_model_flat_4, "tli"),
                  fitmeasures(fit_model_flat_4, "cfi"),
                  fitmeasures(fit_model_flat_4, "aic"),
                  
                  fitmeasures(fit_model_hier_4, "df"),
                  fitmeasures(fit_model_hier_4, "chisq"),
                  fitmeasures(fit_model_hier_4, "rmsea"),
                  fitmeasures(fit_model_hier_4, "rmsea.ci.lower"),
                  fitmeasures(fit_model_hier_4, "rmsea.ci.upper"),
                  fitmeasures(fit_model_hier_4, "srmr"),
                  fitmeasures(fit_model_hier_4, "tli"),
                  fitmeasures(fit_model_hier_4, "cfi"),
                  fitmeasures(fit_model_hier_4, "aic")
                  ), 
                    ncol=9,byrow=TRUE)

#df4, chi-sq3, RMSEA32, RMSEACIUp, RMSEACILow, SRMR28, TFI10, CFI9, AIC 
colnames(Fit_table) <- c("df", "Chi-Sq", "RMSEA","RMSEA CI Lower", "RMSEA CI Upper", "SRMR", "TLI", "CFI", "AIC")
rownames(Fit_table) <- c("1-Factor",
                         "4-Factor", "4-Factor Hierarchial")
Fit_table <- round(Fit_table,3)
```

```{r Fit table, echo=FALSE}
as_tibble(Fit_table) %>% 
  add_column(c("1 Factor", "4 Factor", "4 Factor Hierarchical"), .before = "df") %>%
     rename(Model = `c("1 Factor", "4 Factor", "4 Factor Hierarchical")`) %>% 
     flextable() %>% 
  bold(i = 2:3,
       part = "body") %>% 
  autofit()

```

```{r Model Comparisons, include=FALSE}


#models with all the same items 
test_all<-anova(fit_model_flat,
      fit_model_flat_4,
      fit_model_hier_4)
test_all

#sig here means nested model (hierarhcial) is sig worse than non-nested model

#but note there's not a great way statistically to compare CFA models... 

#test only single factor and four factor

test_2<-anova(fit_model_flat,
      fit_model_hier_4)



```

```{r model comparison anova, echo=FALSE}
test_2
```

