---
title: "DEEP CTN EFA (Pilot 3 SONA Win/Spr23)"
author: Deb Lindsay
date: "`r Sys.Date()`"
slug: efa_sona23
categories:
  - EFA
tags:
  - Connection to Nature
  - DEEP CTN Scale
subtitle: ''
summary: ''
authors: []
lastmod: "`r Sys.Date()`"
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: yes
projects: []
output:
  blogdown::html_page:
    toc: true
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

```{r Packages and Functions required, include=FALSE}

library(tidyverse) #base package that runs most functions
library(Hmisc) #correlations
library(corrplot) #correlations
library(DataExplorer) #Data exploration
library(SmartEDA) #Data exploration
library(ggpubr) #Data exploration
# library(dlookr) #Data exploration (not available in this version)
library(flextable) #tables
library(corpcor) #Factor analysis
library(GPArotation) #Factor analysis
library(psych) #Factor analysis
library(lavaan)#Factor analysis
```

```{r loading data, include=FALSE}
pilot_SONA <-
  read_csv("pilot2SONA_data_clean.csv")

items <-
  read_csv("item names_p2.csv")

```

This is the third pilot study testing the factor structure of the new
CTN scale. Pilot data was collected using SONA from February - April 2023

# Sample Descriptives {.tabset}

```{r Demographics, echo=FALSE}
pilot_SONA<-
  pilot_SONA %>% 
  mutate(age = as.numeric(age))

pilot_SONA$gender <- 
  factor(pilot_SONA$gender, levels = c("man", "woman", "trans man", "trans woman", "non-binary", "other", "no_answer"))

demos <-
pilot_SONA %>% 
  ExpCustomStat(Cvar = "gender", Nvar = "age", stat = c("mean", "count"), gpby = TRUE)

n <- length(pilot_SONA$id)
m_age <-round(mean(pilot_SONA$age),2)
sd_age <-round(sd(pilot_SONA$age),2)
min_age <- min(pilot_SONA$age)
max_age <- max(pilot_SONA$age)

m_pol <- paste(round(mean(pilot_SONA$politics_1, na.rm = T),2))
sd_pol <- paste(round(sd(pilot_SONA$politics_1, na.rm = T),2))

m_ses <- round(mean(pilot_SONA$SESpeer, na.rm = T), 2)
sd_ses <- round(sd(pilot_SONA$SESpeer, na.rm = T), 2)

```

Total sample size was N = `r paste(n)` . The mean age of sample
was `r paste(m_age)`(`r paste(sd_age)`). Age range:
`r paste(min_age)` - `r paste(max_age)`

Political Ideology was scored on a 7-point Likert scale with 1 = Most
Conservative and 7 = Most Liberal. The mean political ideology was
`r paste(m_pol)`(`r paste(sd_pol)`), showing that this sample is skewing
slightly more left-leaning.

SES was scored using the SES Ladder, with 1 being the worst off, and 10 being the best off. Mean sample was `r paste(m_ses)`(`r paste(sd_ses)`).

```{r agegraph, echo=FALSE, message=FALSE, warning=FALSE}

pilot_SONA %>% 
  ggplot() +
  geom_histogram(aes(age)) +
  theme_minimal()

```

```{r polgraph, echo=FALSE, message=FALSE, warning=FALSE}

pilot_SONA %>% 
  ggplot() +
  geom_density(aes(politics_1)) +
  scale_x_continuous(breaks = c(1:7)) +
  theme_minimal()

```

```{r sesgraph, echo=FALSE, message=FALSE, warning=FALSE}

pilot_SONA %>% 
  ggplot() +
  geom_density(aes(SESpeer)) +
  scale_x_continuous(breaks = c(1:10)) +
  theme_minimal()

```

Gender and ethnoracial demographics are reported in the tables below.

```{r gender table, include=FALSE}
desc_table <-
pilot_SONA %>% 
     group_by(gender) %>% 
     summarise(n = length(id),
               `Age(mean)` = round(mean(age, na.rm = T),2),
              `Age(sd)` = ifelse(is.na(sd(age, na.rm=T)), print(NaN), print(round(sd(age, na.rm = T),2)))) 

```

::: row
::: {.col-xs-12 .col-md-6}
```{r printdesctable, echo=FALSE, message=FALSE, paged.print=FALSE}
 
     flextable(desc_table) %>% 
  autofit() 
     #%>% 
 # set_caption(caption = "Gender")

```



`r officer::run_columnbreak()`
:::

::: {.col-xs-12 .col-md-6}
```{r race, echo=FALSE}

str(pilot_SONA$ethnoracial)

pilot_SONA %>% 
     group_by(ethnoracial) %>% 
     summarise(n = length(id)) %>% 
  mutate(ethnoracial = factor(ethnoracial, 
                              levels = c(1:9), 
                              labels = c("Asian", "White", "Hispanic/Latinx", "Black", "Middle Eastern", "Pacific Islander", "First Nation/Indigenous", "Mixed", "No response"))) %>% 
     flextable() %>% 
  autofit() #%>% 
 # set_caption(caption = "Ethnoracial")

```
:::
:::

<!---BLOCK_MULTICOL_STOP{widths: [4,2], space: 0.1, sep: false}--->

# Variables

```{r list of variables, echo=FALSE}
final_items <-
  items %>% 
  filter(Item_code != "AIMES_18" &
           Item_code != "AIMES_19" &
           Item_code != "AIMES_9" &
           Item_code != "AIMES_10" &
           Item_code != "AIMES_11")


final_items %>% 
  flextable() %>% 
  autofit()
  
```

# Assumption Checks

## Correlations between variables

Presented in order of suspected dimensions

```{r Description of Variables, echo=FALSE}
#arrange in order of predicted dimensions
col_order <- c("AIMES_4", "AIMES_1",  "DISPO_29", "DISPO_21", "DISPO_22", "DISPO_34", 
                "DISPO_37", "DISPO_16", 
               "AIMES_8", "AIMES_6", "AIMES_5", 
               "AIMES_9", "AIMES_10", "AIMES_11",
                "DISPO_28", "DISPO_8", "DISPO_13",  "DISPO_33", "DISPO_19", "DISPO_1",  "DISPO_20", "NEW_5", "DISPO_7", "DISPO_23", 
               "DISPO_2", "DISPO_10", "DISPO_11", "DISPO_12", "DISPO_15", "NEW_6", "NEW_7", "NEW_8", "NEW_11", "NEW_12",
               "AIMES_17", "NEW_1", "NEW_10", "NEW_2", "SPIRIT_10", "SPIRIT_12", "AIMES_18", "AIMES_19", "AIMES_20")

factor_order <-
  pilot_SONA[, ..col_order]

factor_order <-
  factor_order %>% 
  select(-AIMES_18,
         -AIMES_19,
         -AIMES_9,
         -AIMES_10,
         -AIMES_11)


#correlation
big_corr <-
factor_order %>% 
  as.matrix() %>% 
  rcorr()

corrplot(big_corr$r, method = "shade", type = "upper", tl.cex = .35, tl.col = "black", number.cex = .35,  number.digits = 2, 
         p.mat = cor.mtest(factor_order)$p, sig.level = 0.01, insig = "blank")


```

## Determinant V1

Check on the whether the model will be overdetermined Should aim for a
determinant \> .00001 (Field et al., 2012)

```{r EFA pre-tests, echo=FALSE}

#find the determinant of our matrix - to see if our matrix is too intercorrelated
#it may be overdetermined
determined <- 
format.pval(det(big_corr$r), eps = .00001, scientific = F)



```

Our model may be overdetermined. Determinant `r paste(determined)`

With more variables included there is the danger for multi-collinearity.
First step is to remove items that have a correlation =\>0.8

No items had a high colinearity

```{r multi-collinear variables, include=FALSE}
#Use the correlation matrix that I created earlier - big_corr$r

#correlations over 0.8
 round(big_corr$r, 2) %>% 
  as.data.frame() %>%
   rownames_to_column %>%
    gather(colname, value, -rowname) %>%
    filter(abs(value) < 1) %>% 
  arrange(desc(value)) %>% 
  flextable() %>% 
  add_header_lines(values = "Correlations > .8") %>% 
  autofit()
 
```

Look at other items that might be a problem...

## Shared Variance

Ensuring there is shared variance between items (Bartlett's test of
sphericity)

```{r bartletts test, echo=FALSE, warning=FALSE, tidy=TRUE}

bartlet <- cortest.bartlett(factor_order) 

bartlet_p <- format.pval(bartlet$p.value, eps = 0.001)

```

Overall, our data is suitable for factor analysis (p value \<.001 are
adequate) $\chi^2$=
`r paste(round(bartlet$chisq,2))`(`r paste(bartlet$df)`) *p* =
`r paste(bartlet_p)`

## Proportion of Variance

(KMO test) Measures the amount of variance in items

```{r KMO test, echo=FALSE, tidy=TRUE}
kmo <- KMO(r=cor(factor_order))
kmo_msa <- round(kmo$MSA,3)

new_cols <- c("AIMES_4","AIMES_1", "DISPO_29", "DISPO_21", "DISPO_22", "DISPO_34",
              "DISPO_37", "DISPO_16", "AIMES_8", "AIMES_6", "AIMES_5", "DISPO_28",
              "DISPO_8", "DISPO_13", "DISPO_33", "DISPO_19", "DISPO_1", "DISPO_20", 
              "NEW_5", "DISPO_7", "DISPO_23", "DISPO_2", "DISPO_10", "DISPO_11",
              "DISPO_12", "DISPO_15", "NEW_6", "NEW_7","NEW_8", "NEW_11", "NEW_12",
              "AIMES_17", "NEW_1", "NEW_10", "NEW_2", "SPIRIT_10", "SPIRIT_12", "AIMES_20")

kmo_items <-
as.matrix(kmo$MSAi) %>% 
  round(2) %>% 
  as.data.frame() %>% 
  add_column(new_cols, .before = "V1") 

colnames(kmo_items) <- c("Item", "KMO")

```

Overall, our data is suitable for factor analysis (overall MSA \> 0.8
are adequate). Data MSA = `r paste(kmo_msa)`

No single item is also less than .80

```{r kmo concern, echo=FALSE}
kmo_items %>% 
    arrange(desc(KMO)) %>% 
  flextable() %>% 
  autofit()
```

## Ceiling and Floor Items

```{r box1, echo=FALSE}
boxplot(factor_order[,c(1:8)],
        las = 2)
```

```{r box2, echo=FALSE}
boxplot(factor_order[,c(9:17)],
        las = 2)
```

```{r box3, echo=FALSE}
boxplot(factor_order[,c(18:26)],
        las = 2)
```


```{r box4, echo=FALSE}
boxplot(factor_order[,c(27:34)],
        las = 2)
```

```{r box5, echo=FALSE}
boxplot(factor_order[,c(34:38)],
        las = 2)
```

## Skewedness

We can also look at the distribution of variables to remove any items
that have a high skewedness Presented in order of suspected dimensions

```{r distribution, echo=FALSE, paged.print=TRUE}
#plot of distribution
plot_histogram(factor_order)

```

After looking at these, no items appear to be need to be removed. Even though the model may be overdetermined, we will run the EFA

# Exploratory Factor Analysis

How many factors can we extract

```{r EFA, include=FALSE}

eigens <-
  eigen(cor(factor_order))

# eigens$values
# uncomment to view the individual eigenvalues

scree(factor_order, pc=FALSE)

parallel <- 
fa.parallel(factor_order, fa = "fa")



```

```{r n factors, echo=FALSE}
scree(factor_order, pc=FALSE)
plot(parallel,)

```

Scree plot suggest \~3-4 factors Parallel factor suggests `r paste(parallel$nfact)` factors
Based on past samples, we will start at 6 factors

# 6 Factors

```{r 6 factors efa, include=FALSE}

fit_6 <- 
  fa(factor_order, 6, rotate="promax", fm= "pa") %>% 
  fa.sort

loadings_6 <- fit_6$loadings
lambda_6 <- unclass(loadings_6)
p6 <- nrow(lambda_6)
factors6 <- ncol(lambda_6)

vx6 <- colSums(loadings_6^2)
varex6 <- rbind(`SS loadings` = vx6)

if (is.null(attr(loadings_6, "covariance"))) {
  varex6 <- rbind(varex6, `Proportion Var` = vx6/p6)
  if (factors6 > 1) 
    varex6 <- rbind(varex6, `Cumulative Var` = cumsum(vx6/p6))
}

factor6_var_table <-
tibble::rownames_to_column(as.data.frame(varex6), "x") %>%  #variance table
flextable()

cutoff <- 0.01 # (the default for the `print.loadings()` function)
fx6 <- setNames(lambda_6, attributes(lambda_6)$dimnames[1])
fx6[abs(lambda_6) < cutoff] <- NA_real_
fx6 <- as.data.frame(fx6)

factor6_load_table <- fx6 #loadings table

comm_6 <- fit_6$communality
cx6 <- setNames(comm_6, attributes(comm_6)$names)
cx6 <- as.data.frame(cx6)  
  
#binding loadings with communalities
factor6_table <- cbind(fx6, cx6) %>% 
  rownames_to_column("item") %>% 
  flextable()

                            
```

```{r 6 factor loading table, echo=FALSE}
factor6_table %>% 
  autofit() %>% 
  color(color = "grey", 
        i = ~ PA1 <.4, 2) %>% 
  color(color = "grey", 
        i = ~ PA4 <.4, 3) %>% 
  color(color = "grey", 
        i = ~ PA3 <.4, 4) %>% 
  color(color = "grey", 
        i = ~ PA5 <.4, 5) %>% 
  color(color = "grey", 
        i = ~ PA2 <.4, 6) %>% 
  color(color = "grey", 
        i = ~ PA6 <.4, 7) %>% 
  colformat_double(digits = 3)

factor6_var_table %>% 
  autofit() %>% 
  colformat_double(digits = 3)
```

# 5 factors

```{r 5 factors EFA, echo=FALSE}
#principal axis (for non-normal data)
fit_5 <- 
  fa(factor_order, 5, rotate="promax", fm= "pa") %>% 
  fa.sort

loadings_5 <- fit_5$loadings
lambda_5 <- unclass(loadings_5)
p5 <- nrow(lambda_5)
factors5 <- ncol(lambda_5)

vx5 <- colSums(loadings_5^2)
varex5 <- rbind(`SS loadings` = vx5)

if (is.null(attr(loadings_5, "covariance"))) {
  varex5 <- rbind(varex5, `Proportion Var` = vx5/p5)
  if (factors5 > 1) 
    varex5 <- rbind(varex5, `Cumulative Var` = cumsum(vx5/p5))
}

factor5_var_table <-
tibble::rownames_to_column(as.data.frame(varex5), "x") %>%  #variance table
flextable()

cutoff <- 0.01 # (the default for the `print.loadings()` function)
fx5 <- setNames(lambda_5, attributes(lambda_5)$dimnames[1])
fx5[abs(lambda_5) < cutoff] <- NA_real_
fx5 <- as.data.frame(fx5)

factor5_load_table <- fx5 #loadings table

comm_5 <- fit_5$communality
cx5 <- setNames(comm_5, attributes(comm_5)$names)
cx5 <- as.data.frame(cx5)  
  
#binding loadings with communalities
factor5_table <- cbind(fx5, cx5) %>% 
  rownames_to_column("item") %>% 
  flextable()


```


```{r 5 factor loading table, echo=FALSE}
factor5_table %>% 
  autofit() %>% 
  color(color = "grey", 
        i = ~ PA1 <.4, 2) %>% 
  color(color = "grey", 
        i = ~ PA4 <.4, 3) %>% 
  color(color = "grey", 
        i = ~ PA3 <.4, 4) %>% 
  color(color = "grey", 
        i = ~ PA5 <.4, 5) %>% 
  color(color = "grey", 
        i = ~ PA2 <.4, 6) %>% 
  colformat_double(digits = 3)



factor5_var_table %>% 
  autofit() %>% 
  colformat_double(digits = 3)


```

# 4 factors

```{r 4 factors EFA , echo=FALSE}

#principal axis (for non-normal data)
fit_4 <- 
  fa(factor_order, 4, rotate="promax", fm= "pa") %>% 
  fa.sort

loadings_4 <- fit_4$loadings
lambda_4 <- unclass(loadings_4)
p4 <- nrow(lambda_4)
factors4 <- ncol(lambda_4)

vx4 <- colSums(loadings_4^2)
varex4 <- rbind(`SS loadings` = vx4)

if (is.null(attr(loadings_4, "covariance"))) {
  varex4 <- rbind(varex4, `Proportion Var` = vx4/p4)
  if (factors4 > 1) 
    varex4 <- rbind(varex4, `Cumulative Var` = cumsum(vx4/p4))
}

factor4_var_table <-
tibble::rownames_to_column(as.data.frame(varex4), "x") %>%  #variance table
flextable()

cutoff <- 0.01 # (the default for the `print.loadings()` function)
fx4 <- setNames(lambda_4, attributes(lambda_4)$dimnames[1])
fx4[abs(lambda_4) < cutoff] <- NA_real_
fx4 <- as.data.frame(fx4)

factor4_load_table <- fx4 #loadings table

comm_4 <- fit_4$communality
cx4 <- setNames(comm_4, attributes(comm_4)$names)
cx4 <- as.data.frame(cx4)  
  
#binding loadings with communalities
factor4_table <- cbind(fx4, cx4) %>% 
  rownames_to_column("item") %>% 
  flextable()


```


```{r 4 factor loading table, echo=FALSE}
factor4_table %>% 
  autofit() %>% 
  color(color = "grey", 
        i = ~ PA1 <.4, 2) %>% 
  color(color = "grey", 
        i = ~ PA3 <.4, 3) %>% 
  color(color = "grey", 
        i = ~ PA4 <.4, 4) %>% 
  color(color = "grey", 
        i = ~ PA2 <.4, 5) %>% 
   colformat_double(digits = 3)



factor4_var_table %>% 
  autofit() %>% 
  colformat_double(digits = 3)


```

Remove items that cross load and fall under the cut-off of .40

```{r 4 factors simple EFA , echo=FALSE}
filtered_factor_4_2 <-
  factor_order %>% 
  select(-NEW_7,
         -DISPO_8,
         -DISPO_1,
         -SPIRIT_12,
         -DISPO_16,
         -DISPO_21,
         -NEW_6,
         -NEW_5,
         -DISPO_23)

#principal axis (for non-normal data)
fit_4_2 <- 
  fa(filtered_factor_4_2, 4, rotate="promax", fm= "pa") %>% 
  fa.sort

loadings_4S <- fit_4_2$loadings
lambda_4S <- unclass(loadings_4S)
p4S <- nrow(lambda_4S)
factors4S <- ncol(lambda_4S)

vx4S <- colSums(loadings_4S^2)
varex4S <- rbind(`SS loadings` = vx4S)

if (is.null(attr(loadings_4S, "covariance"))) {
  varex4S <- rbind(varex4S, `Proportion Var` = vx4S/p4S)
  if (factors4S > 1) 
    varex4S <- rbind(varex4S, `Cumulative Var` = cumsum(vx4S/p4S))
}

factor4_var_tableS <-
tibble::rownames_to_column(as.data.frame(varex4S), "x") %>%  #variance table
flextable()

cutoff <- 0.01 # (the default for the `print.loadings()` function)
fx4S <- setNames(lambda_4S, attributes(lambda_4S)$dimnames[1])
fx4S[abs(lambda_4S) < cutoff] <- NA_real_
fx4S <- as.data.frame(fx4S)

factor4_load_tableS <- fx4S #loadings table

comm_4S <- fit_4_2$communality
cx4S <- setNames(comm_4S, attributes(comm_4S)$names)
cx4S <- as.data.frame(cx4S)  
  
#binding loadings with communalities
factor4_tableS <- cbind(fx4S, cx4S) %>% 
  rownames_to_column("item") %>% 
  flextable()


```

```{r 4 factor SIMP loading table, echo=FALSE}
factor4_tableS %>% 
  autofit() %>% 
  color(color = "grey", 
        i = ~ PA1 <.4, 2) %>% 
  color(color = "grey", 
        i = ~ PA4 <.4, 3) %>% 
  color(color = "grey", 
        i = ~ PA3 <.4, 4) %>% 
  color(color = "grey", 
        i = ~ PA2 <.4, 5) %>% 
   colformat_double(digits = 3)



factor4_var_tableS %>% 
  autofit() %>% 
  colformat_double(digits = 3)


```

# Fit Indices

Comparing the fit of the three models

[*Sources for fit indices*](https://en.wikipedia.org/wiki/Confirmatory_factor_analysis)

```{r fit indices, include=FALSE}
# create a table with five columns (RMSR, TLI, RMSEA, BIC + heading)
# 5 rows (1 for each factor + heading)

#cutoffs:
# fit_6_prolific
# fit_5_prolific
# fit_4_prolific
# fit_4_prolific2

# (CHI sq + df), (RMSEA + CI), (TLI), (RMSR), (BIC) 
chi6 <- fit_6$chi
df6 <- fit_6$dof
rmsea6 <- fit_6$RMSEA[1]
rmsea_ciL6 <- fit_6$RMSEA[2]
rmsea_ciU6 <- fit_6$RMSEA[3]
rmsr6 <- fit_6$rms
tli6 <- fit_6$TLI
bic6 <- fit_6$BIC

chi5 <- fit_5$chi
df5 <- fit_5$dof
rmsea5 <- fit_5$RMSEA[1]
rmsea_ciL5 <- fit_5$RMSEA[2]
rmsea_ciU5 <- fit_5$RMSEA[3]
rmsr5 <- fit_5$rms
tli5 <- fit_5$TLI
bic5 <- fit_5$BIC

chi4 <- fit_4$chi
df4 <- fit_4$dof
rmsea4 <- fit_4$RMSEA[1]
rmsea_ciL4 <- fit_4$RMSEA[2]
rmsea_ciU4 <- fit_4$RMSEA[3]
rmsr4 <- fit_4$rms
tli4 <- fit_4$TLI
bic4 <- fit_4$BIC

chi4S <- fit_4_2$chi
df4S <- fit_4_2$dof
rmsea4S <- fit_4_2$RMSEA[1]
rmsea_ciL4S <- fit_4_2$RMSEA[2]
rmsea_ciU4S <- fit_4_2$RMSEA[3]
rmsr4S <- fit_4_2$rms
tli4S <- fit_4_2$TLI
bic4S <- fit_4_2$BIC

#(CHI sq + df),(RMSEA + CI), (TLI), (RMSR), (BIC) 
Fit_table <- matrix(c( df6, chi6, rmsea6, rmsea_ciL6, rmsea_ciU6, rmsr6, tli6, bic6,
                       df5,chi5, rmsea5, rmsea_ciL5, rmsea_ciU5, rmsr5, tli5, bic5,
                       df4,chi4, rmsea4, rmsea_ciL4, rmsea_ciU4, rmsr4, tli4, bic4,
                       df4S, chi4S, rmsea4S, rmsea_ciL4S, rmsea_ciU4S, rmsr4S, tli4S, bic4S), 
                    ncol=8,byrow=TRUE)

#(CHI sq + df),(RMSEA + CI), (TLI), (RMSR), (BIC)
colnames(Fit_table) <- c( "df","Chi-Sq", "RMSEA","RMSEA CI Lower", "RMSEA CI Upper", "RMSR","TLI",  "BIC")
rownames(Fit_table) <- c("6-Factor",
                         "5-Factor", 
                         "4-Factor",
                         "4-Factor Simplified")
Fit_table <- round(Fit_table,3)

```

```{r Fit table, echo=FALSE}
as_tibble(Fit_table) %>% 
  add_column(c("6-Factor",
                         "5-Factor", 
                         "4-Factor",
                         "4-Factor Simplified"), .before = "df") %>%
     rename(Model = `c("6-Factor", "5-Factor", "4-Factor", "4-Factor Simplified")`) %>% 
     flextable()
```

# Final Assumptions

```{r Assumptions 2, include=FALSE}
simp4_KMO <- 
  round(KMO(r=cor(filtered_factor_4_2))$MSA, 3)


simp4_bart <-
  cortest.bartlett(filtered_factor_4_2)

simp4_bart_p <- format.pval(simp4_bart$p.value, eps = 0.001)


simp4_big_corr <-
filtered_factor_4_2 %>% 
  as.matrix() %>% 
  rcorr()

simp4_det <-
  format.pval(det(simp4_big_corr$r), eps = .00001, scientific = F)


```

Check on the whether the model will be overdetermined Should aim for a
determinant \> .00001 (Field et al., 2012)

Our model may be overdetermined. Determinant `r paste(simp4_det)`, even though we have removed items with high covariance.

Ensuring there is shared variance between items (Bartlett's test of
sphericity). Overall, our data is suitable for factor analysis (p value \<.001 are
adequate) $\chi^2$=
`r paste(round(simp4_bart$chisq,2))`(`r paste(simp4_bart$df)`) *p* =
`r paste(simp4_bart_p)`

Overall, our data is suitable for factor analysis (overall MSA \> 0.8
are adequate). Data MSA = `r paste(simp4_KMO)`