---
abstract: "Connection to Nature (CTN) is a deeply held identity that includes nature in the self. Recent studies suggest a multi-dimensional structure; however, the dimensional structure is still unclear. We propose four dimensions to describe CTN - 1) A deeply held spiritual identity; 2) the experiential relationship with nature; 3) an emotional relationship with nature; and 4) mindful engagement with nature. This poster presents the results of two studies which validate these dimensions. Study 1 suggests a four-dimensional structure using exploratory factor analysis (n = 1,152). Study 2 confirms this using confirmatory factor analysis (n = 341), suggesting a four-dimensional structure has better fit (RMSEA = 0.07, 95%CI = 0-0.9) than a unidimensional structure (RMSEA = 0.10, 95%CI = 0 - 0.9). We also show convergent validity with Connectedness to Nature (Mayer & Frantz, 2004) (r­_deep = .73**, r_exp = .57**, r_emo = .45**, r_pres = .46**), Environmental Identity (Clayton et al., 2021) (r­_deep = .61**, r_exp = .77**, r_emo = .54**, r_pres = .50**), and predictive validity with pro-environmental behaviors (r_deep = .46**, r_exp = .39**, r_emo = .45**, r_pres = .42**)." 

authors:
  - admin
  - Karen Dobkins
date: "`r Sys.Date()`"
doi: ""
featured: true
image:
  caption: "To download full poster, see links above"
  focal_point: ""
  preview_only: false
projects:
publication: SPSP Conference 2024
publication_short: 
publication_types:
  - paper-conference
  - article
list_format: 2
publishDate: "`r Sys.Date()`"
summary: Poster Presentation at SPSP Conference 2024, San Diego
tags: 
  - Connection to Nature
  - DEEP CTN Scale
  - Pro-Environmental Behavior
title: "Going Deeper: Validation of the DEEP Connection to Nature Scale"
url_poster: "pdf/SPSP24_poster.pdf" 
url_project: ""
links:
  - name: OSF
    url: "https://osf.io/5xbvp/" 
bibliography: references.bib
output:
  blogdown::html_page:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

```{r Packages and Functions required, include=FALSE}

library(tidyverse) #base package that runs most functions
library(flextable) #tables
library(moments) #skewness & kurtosis
library(lavaan) #CFA 
library(corrplot) #correlations
library(MVN) #test of normality
library(semPlot) #plotting paths in CFA
library(Hmisc) #correlations 
library(car) # Type 2 Anova
library(effectsize) #effect sizes
library(ggplot2) #plots
library(knitr) #make life easier for tables
library(kableExtra) # better tables (hopefully?)
```

```{r loading data, include=FALSE}
efa_1 <-
  read_csv("pilot1_data_clean.csv")

efa_2 <-
  read_csv("pilot2_data_clean.csv")

efa_3 <-
  read_csv("pilot3SONA_data_clean.csv")

cfa_4 <-
  read_csv("pilot4_cfa_data_clean.csv")

```

# Background

There have been many iterations of a Connection to Nature (CTN) measure (see Ives et al., 2017, Restall & Conrad, 2015, and Tam 2013 for review).
Several of these measures have proposed multi-dimensional structure [@davis2011; @dong2020; @hatty2020; @kurth2020; @meis-harris2021; @olivos2011], however there is little consistency across these dimensional structures.
We build upon two recently published measures [@hatty2020 and @meis-harris2021], which ground their dimensional structure in a thorough cross-disciplinary review of the nature connectedness literature.
We extend their findings by addressing concerns that measures of CTN are vulnerable to self-report biases.
In particular, concerns have been raised that people may be more likely to endorse CTN items out of social desirability or may simply not be able to express the abstract concept of connection to nature when asked directly [@gould2021].
A possible solution to these issues is proposed by the Disposition to Connect with Nature measure which asks about people’s bonding behavior with nature instead of simply asking about preferences to being in nature [@brügger2011].
We adapted items from the Multi-dimensional CTN scale [@meis-harris2021] and the Disposition to Connect with Nature scale [@brügger2011] as well as including several items that we felt addressed the concerns raised about self-report bias.

Across the three exploratory factor analyses, four factors consistently arose as both the best fitting model and aligning with our theoretical framework.
We further tested these four factors in a confirmatory factor analysis with a fourth sample and found adequate fit.
The dimensions include:

1.  Deep (deeply seeing the self as part of nature)
2.  Experiential (spending and enjoying time in nature)
3.  Emotional (Emotional desire to connect with nature and protect it.)
4.  Presence (engaging mindfully and consciously with nature)

# Selecting Initial Items

## Search of existing scales

An extensive search of the literature was conducted to source all existing adult measures of CTN.
Based on this search, we identified two measures that showed promise for further adaptation: The AIMES Multidimensional CTN Scale [@meis-harris2021] and the Disposition to Connect with Nature scale [@brügger2011].
Our search identified that a multi-dimensional structure should be maintained for the measure, however existing multi-dimensional measures showed conflicting dimensional structure.
(@hatty2020 & @meis-harris2021 - the later having a more complex and theoretically driven dimensional structure which is why it was chosen to retain for adaptation).
The Disposition to Connect with Nature scale addressed issues of self-report bias though given it was written for a European sample the items were not generalizable to other populations.
The items from these two scales resulted in a total of 59 items (AIMES = 19 items; Dispositional CTN = 40 items).
Items were reworded for generalizability and clarity.
Any reference to “connection to nature” was removed to avoid concerns about participants not fully understanding this concept.
Items were also removed if they were redundant.
This left a total of 39 items adapted from existing measures (AIMES = 17 items; Dispositional CTN = 28).
See Table 1 below for all items considered for inclusion in the DEEP Connection to Nature Scale.

## Development of new items

We chose to build upon the strong theoretical basis for the dimensional structure of the AIMES with some changes.
@meis-harris2021 based the dimension of the AIMES (Affection, Identity, Materialism, Experience, & Spirituality) off @ives2018 which lists five aspects of human-nature relationships that can lead to behavioral change.
We agree with that three of these dimensions are part of the construct of CTN (these are also widely agreed to be part of the construct of CTN in the literature):

1.  Experiential (time spent in nature)
2.  Cognitive (beliefs about the self’s relationship with nature)
3.  Emotional (affective relationship with nature).

However, they included two value-based dimensions which, while strongly correlated to CTN, have been defined as separate constructs [@schwartz1992; @schwartz1999; @schultz2001; @stern1994]:

4.  Material values towards nature (viewing nature as a resource for human extraction e.g., extrinsic values)
5.  Philosophical views of nature (viewing humans as interrelated with nature e.g., universal values)

We chose to remove the the material dimension entirely and adapt the philosophical dimension so it more accurately reflected the individual level of CTN.
That is, it measured one’s own beliefs about how, as an individual, they are connected to nature.
In line with this re-analysis of the construct of CTN we further adapted the existing 39 items and created an additional 14 items in order to capture the following dimensions of CTN:

1.  Experiential
2.  Cognitive
3.  Emotional
4.  Spiritual (formerly philosophical)

Items were created to capture, behavioral, embodied, and experiential relationships with nature (in line with Brügger et al., 2011’s Disposition to CTN) in order to overcome concerns with self-report bias.
This resulted in items that asked about conscious attendance to nature.
There was also an effort to create items that updated previous philosophical items to more individual relationships with nature which tapped into a more spiritual relationship.
This resulted in a total of 58 items.

**Table 1. Items considered for inclusion in the DEEP Connection to Nature Scale**

```{r tab:1, echo=FALSE, message=FALSE, warning=FALSE}

items <- read_csv("items.csv", na = " ")

items %>% 
  select(`Original Scale`, `Original Item`, Reworded, Notes) %>% 
  kbl(format = "html", 
     label = "tab:1",
     booktabs = T,
     longtable = T) %>% 
  kable_styling(bootstrap_options = "responsive", fixed_thead = T) %>% 
  scroll_box(height = "350px")
  
```

# Exploratory Factor Analysis

## Sample

Two general population Prolific samples and one student sample were collected from November 2022 until April 2023 (See Table 2 for details of these samples)Three exploratory factor analyses were conducted on these samples.

**Table 2. Sample details across three exploratory factor analyses**

|              | Sample 1 (Prolific Nov 22) | Sample 2 (Prolific Apr 23) | Sample 3 (SONA Jan-Apr 23) |
|----------------|:-----------------:|:-----------------:|:-----------------:|
| N            |            575             |            578             |            485             |
| Age          |        29.61(6.11)         |        20.37(2.38)         |        40.56(13.5)         |
| **Gender**   |                            |                            |                            |
| Male         |            283             |            257             |            113             |
| Female       |            256             |            294             |            360             |
| Trans man    |             6              |             7              |             0              |
| Trans woman  |             1              |             2              |             1              |
| Non-binary   |             24             |             11             |             11             |
| No response  |             5              |             6              |             0              |
| **Race**     |                            |                            |                            |
| White        |            360             |            441             |             89             |
| Black        |             40             |             41             |             9              |
| Asian        |             68             |             31             |            187             |
| Latinx\*     |                            |                            |            130             |
| Mixed race   |             54             |             30             |             46             |
| Other        |             38             |             18             |             21             |
| No response  |             15             |             16             |             3              |
| Politics\*\* |         5.18(1.55)         |         4.81(1.70)         |         5.02(1.14)         |

\*Prolific does not capture this racial identity\
\*\*1 (extremely liberal) - 4(middle of the road) - 7(extremely conservative)

## Items Removed

Several items were removed in sample 1 before the EFA was conducted.
These items were also excluded from samples 2 and 3.
Five items were removed due to high collinearity

A test for overdetermination revealed that the model may be overdetermined due to high colinearity between items (det \<.00001).
Inspection of the correlations revealed five items with highly colinearity (see Table 2).
The decision was made to remove AIMES_15, AIMES_7, and AIMES_2.
However, removing these items did not improve the risk of overdetermination (det \<.00001).

Further assumptions were explored to see if other items should be removed.
A Bartlett’s test of sphericity found there was adequate shared variance between items (𝜲2 = 17044.9(1225), p \<.001).
A Kaiser-Meyer-Olkin test of factor adequacy found that, overall, there was adequate variance within items (MSA = 0.97).
However, exploration of individual items identified three items which may not have sufficient variance: DISPO_32, DISPO_38, & DISPO_36 (MSA = 0.89, MSA = 0.82, & MSA = 0.84 respectively).
Inspection for ceiling and floor effects confirms this, as well as identifying several other items that may have limited variance (See Figure 1).
Several items also appeared to have high positive or negative skew (See Figure 2).
Several items were removed due to high skewedness (NEW_9, DISPO_38, DISPO_39, DISPO_6, & DISPO_36).
A final check of overdetermination revealed there is still the potential for the fit to be overdetermined (det \<.00001).

Sample 2

A test for overdetermination revealed that the model may be overdetermined due to high colinearity between items (det \<.00001).
Inspection of the correlations no items with highly colinearity. 

Further assumptions were explored to see if other items should be removed.
A Bartlett’s test of sphericity found there was adequate shared variance between items (𝜲2 = 8385.44(703), p \<.001).
A Kaiser-Meyer-Olkin test of factor adequacy found that, overall, there was adequate variance within items (MSA = 0.95).
Exploration of individual items showed that no single item was \< .80.
Inspection of box plots and histograms of distribution showed not items with ceiling/floor effects or high skewedness.

Sample 3

A test for overdetermination revealed that the model may be overdetermined due to high colinearity between items (det \<.00001).
Inspection of the correlations no items with highly colinearity. 

\
Further assumptions were explored to see if other items should be removed.
A Bartlett’s test of sphericity found there was adequate shared variance between items (𝜲2 = 8353.44(73), p \<.001).
A Kaiser-Meyer-Olkin test of factor adequacy found that, overall, there was adequate variance within items (MSA = 0.95).
Exploration of individual items showed that no single item was \< .80.
Inspection of box plots and histograms of distribution showed not items with ceiling/floor effects or high skewedness.


## Number of Factors

Despite the potential for overdetermination, an EFA was conducted using a principal analysis method of extraction. This method has been found to be robust with models with non-normal data (Briggs & MacCullum, 2003). The Psych package in R was used with a promax rotation and principal analysis factoring method.

The number of factors to be extracted was estimated using both a scree plot and parallel analysis. The screen plot suggested ~3-4 factors, while parallel analysis suggested 6 factors across all three samples

[insert plots here from all three samples]

Four models were run across all three samples:
* Six factors
* Five factors
* Four factors
* Simplified four factors (removing dual loading and poor loading items from four factor model)

[Link to pdf for these tables - all three samples]

## Item Selection Based on Model Fit

The simplified 4-factor model may be still be overdetermined: determinant < 0.00001, even though we have removed items with high covariance.

Tests of shared variance between items and variance within items both suggest the data is suitable for factor analysis. 
Sample 1 - Bartlett’s test of sphericity showed a 𝜲2 = 3171.39(595), p <.001). A Kaiser-Meyer-Olkin test of factor adequacy found that, overall, there was adequate variance within items (MSA = 0.97). 
Sample 2 - Bartlett’s test of sphericity showed a 𝜲2 = 6674.74(406), p <.001). A Kaiser-Meyer-Olkin test of factor adequacy found that, overall, there was adequate variance within items (MSA = 0.95). 
Sample 3 -  Bartlett’s test of sphericity showed a 𝜲2 = 6674.74(406), p <.001). A Kaiser-Meyer-Olkin test of factor adequacy found that, overall, there was adequate variance within items (MSA = 0.95). 


We calculated several fit indices and found that the simplified four-factor model was an appropriate fit across all three samples. While the full four-factor model, shows better fit according to these indices. We chose to keep the simplified factor due to the full four factor model including items that cross loaded.

The root mean square error of the approximate (RMSEA) should aim for > 0.05. The root mean square of the residuals (RMSR) should be close to 0. The Tucker-Lewis Index (TLI) aims for scores > 0.9. The Baysean Information Criteria (BIC) should be smaller and more negative.

[insert table off all sample fit indices]

Based on these results we selected xx items to test in a confirmatory factor analysis.

[go into more details based on EFA Overview document]

[insert table of items tested in CFA here]

# Confirmatory Factor Analysis

## Sample
394 undergraduate students participated for course credit in May 2023. Thirty-one participants did not complete the study and twenty-two people failed to pass attention checks so their data was not analysed. The final analysis consisted of 341 participants with ages ranging from 18 - 42 (M = 20.88, SD = 2.7). The same was primarily made up of females (68.3%) and people of Asian ethnicity (42.1%). See the table below for full descriptive statistics. Political Ideology was scored on a 7-point Likert scale with 1 = Most Conservative and 7 = Most Liberal. The mean political ideology was 5.04(1.17), showing that this sample skewed more liberal. This is to be expected with our student sample.

## Convergent Validity Measures
Two pre-existing CTN scales were used to identify convergent validity. The Connectedenss to Nature Scale (CNS, Mayer & Frantz, 2004) and the Environmental Identity Scale revised (EID-R, Clayton et al., 2021). The CNS is a 14-item scale designed to measure the cognitive beliefs about how interneconnect one’s self is to nature. It is measured on a Likert scale ranging from 1(strongly disagree) to 5(strongly agree). The EID-R is a 14-item scale designed to measure how interneconnect one’s self is to nature. It is measured on a Likert scale ranging from 1(not at all true of me) to 7(completely true of me).

## Predictive Validity measures
### Pro-environmental behavior
Participants completed the Recurring Pro-environmental Behavior scale (Brick et al., 2017) which asks people to report how often they engage in various pro-environmental behaviors. This scale includes 20 items measured on a Likert scale ranging from 1(never) to 5(always).

### Primal Beliefs 
Three subscales of the primals beliefs inventory (Clifton et al., 2019) were used to identify worldviews held by participants. The About Me subscale consists of five questions asking how egocentric ones beliefs are (e.g., Whatever is happening around me often feels related to me or something I’ve done). The Hierarchical subscale consists of five questions exploring beliefs about the hierarchical nature of the world (e.g., Things are rarely equal. Most plants and animals, even people, are better or worse than one another.). The Interconnected subscale consists of four items asking how connected or atomistic one believes the world to be (e.g., Most things are basically unconnected and independent from each other [reversed]). All items are measured on a Likert scale ranging from 1(strongly disagree) to 6(strongly agree).

## Covariate measures
### Locus of Control
Participants completed a brief version of the Locus of Control Scale (Sapp & Harrod, 1993) which includes 9 items revealing how much people perceived they have internal control over events (e.g., To a great extent, my life is controlled by accidental happenings). Measured on a Likert scale from 1(strongly disagree) to 7(strongly agree).

### Demographics
They also answered several demographics questions (age, gender, political  ideology, and social economic status).

## Analysis & Results

### Items Removed
Several assumptions need to be met before running a confirmatory factor analysis. We identified that no item had a high inter-correlation > .75. Next, we checked the skewedness and kurtosis of each item to be included in the CFA. The closer to zero for both skewedness and kurtosis, the closer to a normal distribution. Any items whose distributions exhibited skewness and/or kurtosis that exceed general guidelines were considered non-normal removed from the analysis (Hair et al., 2017, p. 61). 

For skewedness, using the skewness function from the Moments package in R (Komsta & Novemstky, 2015), skewness was calculated for each item. Any item where the number is greater than +1 (right skewed) or lower than -1 (left skewed), this is an indication of a substantially skewed distribution. No items were heavily skewed in this dataset.

For Kurtosis, using the kurtosis function from the Moments package in R (Komsta & Novemstky, 2015), kurtosis was calculated for each item. Any item were the number is greater than +3, the distribution is too peaked. Likewise, a kurtosis of less than -3 indicates a distribution that is too flat. Two items showed high kurtosis: “I have great respect for being alive on this earth and part of the universe” and “Listening to the sounds of nature makes me relax” and were removed from the CFA.

[insert kurtosis figure]

A Mardia Test of multivariate normality from the MVN package in R (Korkmaz et al., 2021) indicated that this data is not normal, suggesting that a rotation-method that is robust to non-normal data should be used (Mardia Skewedness = 7681.36, p < .001 and Mardia Kurtosis = 28.32, p < .001).

### Model Fitting
#### Four factor hierachical Model
Testing a structure which includes an overall Connection to Nature factor and four dimensions:

1. Deep: Deeply seeing the self as part of nature
2. Experiential: Spending more time in nature and enjoying spending time in nature
3. Emotional: Emotional desire to connect with nature and protect it
4. Presence: Engaging mindfully and consciously with nature

Items load onto their dimensions well, with the exception of 1 item (“Thinking of someone carving their initials into a tree makes me cringe”) which loaded onto the Emotion dimension at 0.33.

All dimensions loaded onto the single CTN dimension, but these loaded quite highly (especially Deep and Emotion) which suggests these might be driving the overall CTN score.

[insert cfa figure]

#### Four Factor
Testing a structure which only includes the four dimensions:

1. Deep: Deeply seeing the self as part of nature
2. Experiential: Spending more time in nature and enjoying spending time in nature
3. Emotional: Emotional desire to connect with nature and protect it
4. Presence: Engaging mindfully and consciously with nature

Items load onto their dimensions similarly well to the hierarchical model. Again, 1 item loads weakly: (“Thinking of someone carving their initials into a tree makes me cringe”) which loaded onto the Emotion dimension at 0.33.

Dimensions are intercorrelated reasonable well - not too high as to have multi-collinearity (none above .80)

[insert cfa figure]

#### Single Factor
Testing a structure which includes only a single overall Connection to Nature factor

Loadings are slightly weaker onto a single overall CTN factor. Again, 1 item loads weakly: (“Thinking of someone carving their initials into a tree makes me cringe”) which loaded onto the Emotion dimension at 0.31.

[insert cfa figure]

### Item Selection Based on Model Fit
Both four-factor models (flat and hierarchical) perform better than the single-factor model. There is no difference between the hierarchical and the flat models.

[inset fit incides table]

[insert final item table]

# Validation
## Sample
Same sample as Confirmatory Factor Analysis

## Convergent Validity

Two pre-existing CTN scales were used to identify convergent validity. The Connectedenss to Nature Scale (CNS, Mayer & Frantz, 2004) and the Environmental Identity Scale revised (EID-R, Clayton et al., 2021). The CNS is a 14-item scale designed to measure the cognitive beliefs about how interneconnect one’s self is to nature. It is measured on a Likert scale ranging from 1(strongly disagree) to 5(strongly agree). The EID-R is a 14-item scale designed to measure how interneconnect one’s self is to nature. It is measured on a Likert scale ranging from 1(not at all true of me) to 7(completely true of me).

We assessed the convergent validity of the new DEEP CTN scale, that is how closely our new measure is related to other established measures of the same construct. We tested this by looking at the zero order correlation between our new measure and its subscales and two established measures: The Connectedness to Nature Scale (CNS  - Mayer & Franz, 2004) and the Environmental Identity Scale revised (EID-R - Clayton et al., 2021). A zero-order correlation found moderate-strong correlation between existing CTN scales and the new subscales of the DEEP CTN scale. See table below:

[insert table]

## Predictive Validity
Two measures of predictive validity were used: Pro-environmental behavior & three subscales of the primal beliefs invetory - the world is interconnected, the world is heirarchical, and the world is about me. 

Participants completed the Recurring Pro-environmental Behavior scale (Brick et al., 2017) which asks people to report how often they engage in various pro-environmental behaviors. This scale includes 20 items measured on a Likert scale ranging from 1(never) to 5(always).

Three subscales of the primals beliefs inventory (Clifton et al., 2019) were used to identify worldviews held by participants. The About Me subscale consists of five questions asking how egocentric ones beliefs are (e.g., Whatever is happening around me often feels related to me or something I’ve done). The Hierarchical subscale consists of five questions exploring beliefs about the hierarchical nature of the world (e.g., Things are rarely equal. Most plants and animals, even people, are better or worse than one another.). The Interconnected subscale consists of four items asking how connected or atomistic one believes the world to be (e.g., Most things are basically unconnected and independent from each other [reversed]). All items are measured on a Likert scale ranging from 1(strongly disagree) to 6(strongly agree).

We assessed the predictive validity of the new DEEP CTN scale (i.e., how well our measure can predict participant scores on two theoretically related constructs). The “gold standard” for predictive validity of CTN measures is how well it predicts pro-environmental behavior (PEB) (Clayton, 2003; Clayton et al., 2021; Mayer & Frantz, 2004; Tam, 2013). A zero-order correlation found moderate correlations between PEB  and the new subscales of the DEEP CTN scale. See table below:

[insert table]

A linear regression with only the subscales of CTN predicting PEB showed that Deep, Emotional, and Presence were adequate to predcict PEB, but not Experiential.

[insert table & effect sizes]

We also suspected that DEEP CTN and its subscales would predict three types of primal world beliefs (Clifton et al., 2019): That the world is interconnected, that the world is not hierarchical, and that the world is not about me (i.e., less egocentric worldviews).  A zero-order correlation found weak -moderate correlations between interconnected beliefs and the new subscales of the DEEP CTN scale. We also found weak correlations between egocentric beliefs and the Deep, Presence, and Overall CTN. No relationship was found between any subscale and hierarchical worldviews. See table below:

[insert table]

## Incremental Validity

We explored if the DEEP CTN scale and its facets would perform above and beyond existing CTN scales (i.e., CNS and EID-R) when predicting PEB. A linear regression model was run, which included the dimensions of the DEEP CTN scale and the existing CTN measures (CNS and EIDR) were entered simultaneously to predict PEB. Note that because overall CTN was highly intercorrelated with Deep and Emotional, it was left out and only the four dimensions were included. 

We found that the Emotional and Presence subscales remained significant predictors when existing measures of CTN were entered into the model. The Deep subscale was no longer a significant predictor. Both our subscales were of equal predictive value compared to the existing measures.

[insert table & effects figure]


## Covariates
Participants completed a brief version of the Locus of Control Scale (Sapp & Harrod, 1993) which includes 9 items revealing how much people perceived they have internal control over events (e.g., To a great extent, my life is controlled by accidental happenings). Measured on a Likert scale from 1(strongly disagree) to 7(strongly agree). Participants also answered several demographics questions (age, gender, political  ideology, and social economic status).

We also tested the robustness of our new DEEP CTN scale, by testing if the DEEP CTN scale and its facets are significant predictors of PEB after controlling for known covariates of these outcomes: political ideology, gender, and socio-economic status (SES). We fist inspected a zero order correlation to identify which covariates should be included. Including any variable that:
strongly correlated with PEB AND
weakly correlated with the Deep CTN Scale
may reduce variance in the dependent variable and therefore enhance the likelihood of seeing significant effects of the DEEP CTN scale. 
Further, if an additional variable is…
strongly correlated with BOTH PEB AND
the Deep CTN Scale,
its inclusion in the model will address potential mediating effects regarding the relationship between the Deep CTN Scale and a DV of interest. In either case this would suggest it’s important to include as a covariate.


This resulted in including the following covariates:
Politics (r = .19** with PEB & r = .18** to .23** with DEEP CTN dimensions)
Primal Beliefs - The world is interconnect (r = .21** with PEB & r = .22** to .38** with DEEP CTN dimensions)

[insert correlation matrix]

A multiple linear regression model where dimensions of the DEEP CTN scale and existing CTN measures (CNS and EIDR) and the covariates (politics & primal belief interconnectedness) were entered simultaneously to predict PEB is reported in the table below.


By adding the covariates, both Emotional and Prescence subscales remained significant predictors of PEB. Adding covariates to the model did not improve the fit of the model above the variables in the incremental validity model (F(2) = 1.731, p = 0.179).

[insert table & effects figure]

# Discussion
[write up a summary of the findings here]

# References
